---
title: "BES voting patterns study"
subtitle: Exploratory analysis  - draft version 1
author: "Pierre Walthéry"
date: today
date-format: DD MMMM YYYY
format: 
  html:
    embed-resources: true
    page-layout: full
    mainfont: "Open Sans"
    toc: true
    smooth-scroll: true
    toc-location: left
execute:
  warning: false
  message: false
  echo: false
  cache: false
---

```{r data}
# Log hours 1.5 15 May
# 130 min 23 May
# 90 mins 24-26 May  
# 4h max - 26 May
  
rm(list=ls())


library(haven)
library(survey)
library(dplyr)
library(forcats)
library(knitr)
library(gtsummary)
library(ggplot2)

datadir<-"~/Data/bes/"
bes23<-read_dta(paste0(datadir,"BES2019_W23_v25.0.dta"))


#### Necessary for corss sectional voting estimates
# Only need to be run once

# bes01<-read_dta(paste0(datadir,"1997-2001BESPanel.dta"))
# bes05<-read_dta(paste0(datadir,"2005-2009BES6WavePanel.dta"))
# bes10<-read_dta(paste0(datadir,"cipsdec2311.dta"))
# bes15<-read_dta(paste0(datadir,"BES2015_W6_v25.0.dta"))
# bes17<-read_dta(paste0(datadir,"BES2017_W13_v25.0.dta"))
# bes19<-read_dta(paste0(datadir,"BES2019_W21_v25.1.dta"))

#bes21<-read_dta("~/Data/bes/BES2019_W21_v25.1.dta")
# cc_q98

# voted<-list()
# 
# 
# voted[["GE01"]]<-bes01|>select(rage00,sexnr97,voted01,wtallgb) #|> filter(rage00>50)
# names(voted[["GE01"]])<-c("age.r", "gender","p_turnout_2001","wt")
# voted[["GE01"]]$age<-ifelse(b01$age.r==-8 | b01$age.r>95,NA,b01$age.r)
# voted[["GE01"]]$gender.f=droplevels(fct_recode(as_factor(voted[["GE01"]]$gender),
#                    "Male" = "male",
#                    "Female" = "female"))
# voted[["GE01"]]$VotGE01.f=droplevels(fct_recode(as_factor(voted[["GE01"]]$p_turnout_2001),
#                                    "Voted" = "yes, voted",
#                                    "Did not vote/NA" = "no",
#                                    "Did not vote/NA" = "don't   know"
#                                    )
#                          )
# 
# 
# voted[["GE05"]]<-bes05|>select(post_q66,post_q69,post_q63,post_w8) #|> filter(post_q66>50)
# names(voted[["GE05"]])<-c("age", "gender","p_turnout_2005","wt")
# 
# voted[["GE05"]]$gender.f=fct_recode(as_factor(voted[["GE05"]]$gender),
#                                    "Male" = "male",
#                                    "Female" = "female")
# 
# voted[["GE05"]]$VotGE05.f=droplevels(fct_recode(as_factor(voted[["GE05"]]$p_turnout_2005),
#                                     "Voted" = "in person",
#                                     "Voted" = "by post",
#                                     "Voted" = "by proxy",
#                                     "Did not vote/NA" = "did not vote",
#                                     "Did not vote/NA" = "don’t know"
# )
# )
# 
# 
# voted[["GE10"]]<-bes10|>select(cc_q98,ccq100,ccq24,post_w8) #|> filter(post_q66>50)
# names(voted[["GE10"]])<-c("age", "gender","p_turnout_2010","wt")
# voted[["GE10"]]$gender.f=droplevels(fct_recode(as_factor(voted[["GE10"]]$gender),
#                                    "Male" = "male",
#                                    "Female" = "female"))
# voted[["GE10"]]$VotGE10.f=droplevels(fct_recode(as_factor(voted[["GE10"]]$p_turnout_2010),
#                                     "Voted" = "yes, voted",
#                                     "Did not vote/NA" = "no, did not vote",
#                                     "Did not vote/NA" = "don’t know"
# )
# )
# 
# 
# voted[["GE15"]]<-bes15|>select(age,gender,genElecTurnoutRetro,wt ) #|>filter(age>50 & !is.na(wt))
# names(voted[["GE15"]])<-c("age", "gender","p_turnout_2015","wt")
# voted[["GE15"]]$gender.f=as_factor(voted[["GE15"]]$gender)
# 
# voted[["GE15"]]$VotGE15.f=droplevels(fct_recode(as_factor(voted[["GE15"]]$p_turnout_2015),
#                                     "Voted" = "Yes, voted",
#                                     "Did not vote/NA" = "No, did not vote",
#                                     "Did not vote/NA" = "Don't know"
# )
# )
# voted[["GE15"]]$VotGE15.f<-factor(voted[["GE15"]]$VotGE15.f,levels=c("Voted","Did not vote/NA"))
# 
# 
# voted[["GE17"]]<-bes17|>select(age,gender,p_turnout_2017,wt ) #|>filter(age>50 & !is.na(wt))
# names(voted[["GE17"]])<-c("age", "gender","p_turnout_2017","wt")
# voted[["GE17"]]$gender.f=as_factor(voted[["GE17"]]$gender)
# 
# voted[["GE17"]]$VotGE17.f=droplevels(fct_recode(as_factor(voted[["GE17"]]$p_turnout_2017),
#                                     "Voted" = "Yes, I voted",
#                                     "Did not vote/NA" = "No, I did not vote",
#                                     "Did not vote/NA" = "Don't know"
# )
# )
# voted[["GE17"]]$VotGE17.f<-factor(voted[["GE17"]]$VotGE17.f,levels=c("Voted","Did not vote/NA"))
# 
# voted[["GE19"]]<-bes19|>select(age,gender,p_turnout_2019,wt ) #|>filter(age>50 & !is.na(wt))
# names(voted[["GE19"]])<-c("age", "gender","p_turnout_2019","wt")
# voted[["GE19"]]$gender.f=as_factor(voted[["GE19"]]$gender)
# 
# voted[["GE19"]]$VotGE19.f=droplevels(fct_recode(as_factor(voted[["GE19"]]$p_turnout_2019),
#                                                 "Voted" = "Yes, I voted",
#                                                 "Did not vote/NA" = "No, I did not vote",
#                                                 "Did not vote/NA" = "Don't know"
# )
# )
# voted[["GE19"]]$VotGE19.f<-factor(voted[["GE19"]]$VotGE19.f,levels=c("Voted","Did not vote/NA"))
# 
# # # Save the list to an RDS file
# saveRDS(voted, file = "~/Dropbox/work/ELSAwork/data/voted_BES.rds")


voted <- readRDS("~/Dropbox/work/ELSAwork/data/voted_BES.rds")

b23<-bes23|>filter(age>50 & !is.na(wt))

### Variable labels search
  vlab23<-"" 
  for (vr in names(bes23)) { 
  vlab23<-c(vlab23,paste(vr,attr(bes23[[vr]],"label"),sep="----")) 
  } 
  # vlab21<-"" 
  # for (vr in names(bes21)) { 
  #   vlab21<-c(vlab21,paste(vr,attr(bes21[[vr]],"label"),sep="----")) 
  # } 
  # 
  
#res.voted1<-grep("voted",vlab23,fixed=TRUE,value=T)  -->
```


## 1. Introduction
This document presents initial results of an  analysis of the 2019 British Election Study Wave 23 that focuses on General Election turnout among the 50+, looking socio-demographic factors and past voting behaviour, including at the 2005, 2012, 2015,2017,2019 General Elections. 
This study aims to reproduce a similar analysis conducted on the English Longitudinal Study of Ageing (Wave 10).

## 2. Methods
### Sample
Given that fieldwork for  ELSA Wave 10 took place between October 2021 and March 2023,  the BES dataset with the largest overlap  was Wave 23, with fieldwork conducted between the 6th and the 26th of May 2022. 
Overall sample size for those aged over 50 is `{r} length(bes23$age[bes23$age>50])`. Comparability with analysis conducted on ELSA data will be limited due to ageaing-specific variables not present in BES.
On the other hand, given that retrospective questions about vote participation were asked at Wave 23, no observation 
loss  resulting from attrition occurred as would have been the case by linking the data with previous waves.

The outcome variable is voting turnout at the 2019 General Elections.

### Original Variables

Below is the list  of the original variables considered for the analysis.

|Name|Description|Variable label
|----|-----------|------------------------------------:
p_turnout_2019|Whether voted - 2019 GE|2019 GE turnout                   
age|Age|Age of respondent|  
gender|Gender of respondent|Gender
p_disability|Whether disabled| Are your day-to-day activities limited because of a health problem or disabilit
p_education|Education| Education qualification (highest attained)
p_ethnicity|Ethnicity|To which of these groups do you consider you belong?
p_hh_children|Number of <18| How many of the people in your household are under 18?
p_hh_size|Household size| How many people, including yourself, are there in your household?  
p_job_sector|Broad industry|What kind of organisation do you work for?  
p_marital|Marital/relationship status| What is your current marital or relationship status?
p_religion|Religious belonging| Do you regard yourself as belonging to any particular religion, and if so, to w 
ns_sec_analytic|Social class 8 categories| ns-sec analytic categories
p_turnout_2005|Whether voted - 2005 GE|2005 GE turnout                   
p_turnout_2010|Whether voted - 2010 GE|2010 GE turnout                   
p_turnout_2015|Whether voted - 2015 GE|2015 turnout (earliest recorded)                   
p_turnout_2017|Whether voted - 2017 GE|2017 GE turnout                   
p_work_stat|Econ acti/employment status | Which of these applies to you?  
preschoolKidsInHouseW21_|Whether under 6 in the HH| in the Cares for pre-school age children          
schoolKidsInHouseW21_|Whether 6-16 in the HH|Cares for school age children
sickElderlyInHouseW21_|Whether care for adults|Cares for sick, disabled or elderly adults
wt|Cross-sectional weight|New Weight Wave 23
------------------------------------------------------------------------------------------

The following two variables are documented in the W21 dataset but are not actually  present:

|Name|Description|Variable label
|----|-----------|------------------------------------:
eq5d1 (W21)|Mobility| Please choose the option that best describes your health **today** in terms of **mobility**
eq5d2 (W21)| Autonomy| Please choose the option that best describes your health **today** in terms of **self-care**

This would otherwise have presented a good rationale for using W21 instead of W23.

### Derived variables

The following derived variables were created:
  
|Name|Description|Variable label
|--------|-------------------------------|------------------------------------:
  dimarr4|Marital and relationship status, 4 category| Relationship status
  edqual4.f|  Highest educational achievement, 4 category|Highest qualification
  hhdtypb4.f|Household type, 4 category|Household type
  relig.f|Whether religious (any religion)|Whether religious
  VotRec0|Number of times voted in the last 4 general elections|Times voted at the last GEs
  wpdes4.f|Combined work/caring status 4 category|Work + carer status

```{r functions,tidy=T}
source("functions.R")
```



```{r main_rec}
bvars<-c("AgeCat2.f", "AgeCat3.f", "gender.f") 
ivs<-c(
  "dimarr4.f", "disab.f", "edqual4.f", "ethnic.f", 
  "hhdtypb4.f",  "nssec.f","relig.f",   "VotGE05.f", 
  "VotGE10.f", "VotGE15.f","VotGE17.f",  "VotRec0", "wpdes4.f" 
)

ivars<-c(ivs,bvars)

vars<-c(
"AgeCat2.f", "AgeCat3.f",
"dimarr4.f", "disab.f", "edqual4.f", "ethnic.f",  "gender.f",
"hhdtypb4.f", "nssec.f","relig.f",   "VotGE05.f", "VotGE10.f", 
"VotGE15.f","VotGE17.f","VotGE19.f",  "VotRec0", "wpdes4.f" 
)

labs<-list(
  AgeCat2.f="Age 2 categories",
  AgeCat3.f="Age 3 categories",
  dimarr4.f="Relationship status",
  disab.f="Whether daily life limited",
  edqual4.f="Highest qualification",
  ethnic.f="Ethnicity",
  gender.f="Gender",
  hhdtypb4.f="Household type",
  nssec.f="Social class",
  relig.f="Whether religious",
  VotGE05.f="Whether voted (GE 2005)",
  VotGE10.f="Whether voted (GE 2010)",
  VotGE15.f="Whether voted (GE 2015)",
  VotGE17.f="Whether voted (GE 2017)",
  VotGE19.f="Whether voted (GE 2019)",
  VotRec0="Times voted at previous GE",
  wpdes4.f="Work + carer status"     
)
  


b23<-b23|>mutate(
  AgeCat2.f=as.factor(case_when(
    age>=50 & age<70 ~ "50-69",
    age>=70 ~ "70+"
  )),
  gender.f=as_factor(
  gender  
  ),
  AgeCat3.f=as.factor(case_when(
    age>=50 & age<70 ~ "50-69",
    age>=70 & age<80 ~ "70-79",
    age>=80  ~ "80+"
  )),
  wpdes4.f=as.factor(case_when(
    p_work_stat==5 ~ "Retired",
    p_work_stat %in% c(1,2,3) ~ "In employment",
    p_work_stat %in% c(4,6,7,8)  &  sickElderlyInHouseW21_==1 ~ "FT carer + unemp.",
    p_work_stat %in% c(4,6,7,8)  &  p_disability==1  ~ "LT sick/disabled"
  )),
    edqual4.f = as.factor(case_when(
      p_education %in% c(1, 2, 8)                        ~ "Below secondary",
      p_education %in% c(3, 4, 5, 6, 7, 9, 10, 11, 12)   ~ "Secondary",
      p_education %in% c(13, 14, 15, 16, 17, 18)         ~ "Higher education",
      p_education %in% c(19, 20)                         ~ "Other",
      TRUE                                        ~ NA_character_
    )),
  ethnic.f = as.factor(case_when(
    p_ethnicity %in% c(1, 2) ~ "White",
    p_ethnicity %in% c(3, 4, 5, 6) ~ "Mixed",
    p_ethnicity %in% c(7, 8, 9, 10) ~ "Asian",
    p_ethnicity %in% c(11, 12, 13) ~ "Black",
    p_ethnicity %in% c(14, 15) ~ "Other",
    TRUE ~ NA_character_  # includes "Prefer not to say"
  )),
    dimarr4.f=as.factor(case_when(
    p_marital %in% c(1, 2,4,6) ~ "In a relationship",
    p_marital %in% c(3, 7) ~ "Divorced/separated",
    p_marital == 6 ~ "Single",
    p_marital == 8 ~ "Widowed",
    TRUE ~ NA_character_
  )),
  disab.f=fct_recode(as_factor(p_disability),
                   "A lot" = "Yes, limited a lot", 
                    "A little" = "Yes, limited a little", 
                   "No"="No"),
    hhdtypb4.f=as.factor(case_when(
    p_hh_size == 1 ~ "Single person HH",
    p_hh_size == 2 & p_hh_children == 1 ~ "Two adults HH",
    p_hh_children > 1 & p_hh_children < 8 ~ "Family,large/small",
    p_hh_size > 2 & p_hh_children == 1 ~ "3+ adults HH",
    TRUE ~ "Other"
  )),
  nssec.f=as_factor(ns_sec_analytic),
  relig.f = as.factor(if_else(p_religion == 1, "Religious","Not religious")),
  
  # srh4=as.factor(case_when(
  #   hehelf==1  | hehelf==2 ~ "Excel/V. good",
  #   hehelf==3 ~ "Good",
  #   hehelf==4  ~ "Fair",
  #   hehelf==5 ~ "Poor"
  # )),
  # iafcon4=as.factor(case_when(
  #   iafcon==1   ~ "Manage very well",
  #   iafcon==2   ~ "Manage quite well",
  #   iafcon==3   ~ "Get by alright",
  #   iafcon==4 | iafcon==5 | iafcon==6 ~ "Does not manage well"
  # ))
  VotGE19.f = as.factor(if_else(p_turnout_2019==1,"Voted","Did not vote/NA")),
  VotGE05.f = as.factor(if_else(p_turnout_2005 == 1, "Voted","Did not vote/NA")),
  VotGE10.f = as.factor(if_else(p_turnout_2010 == 1, "Voted","Did not vote/NA")),
  VotGE15.f = as.factor(if_else(p_turnout_2015 == 1, "Voted","Did not vote/NA")),
  VotGE17.f = as.factor(if_else(p_turnout_2017 == 1, "Voted","Did not vote/NA")),
  
  # Sum votes across the 4 elections
  total_votes = (p_turnout_2005 == 1) +
    (p_turnout_2010 == 1) +
    (p_turnout_2015 == 1) +
    (p_turnout_2017 == 1),
  
  # Create VotRec0 factor variable
  VotRec0 = as.factor(case_when(
    total_votes == 0 ~ "None",
    total_votes %in% 1:2 ~ "1-2",
    total_votes %in% 3:4 ~ "3-4"
  )),
  VotRec01 = as.factor(case_when(
    total_votes == 0 | total_votes == 1 ~ "None or 1",
    total_votes ==2  ~ "2",
    total_votes %in% 3:4 ~ "3-4"
  ))            
  )

for(var in names(labs)){
  attr(b23[var],"label")<-labs[[var]]
}

attr(b23$disab.f,"label")<-labs[["disab.f"]]
attr(b23$ethnic.f,"label")<-labs[["ethnic.f"]]
attr(b23$nssec.f,"label")<-labs[["nssec.f"]]
attr(b23$relig.f,"label")<-labs[["relig.f"]]
attr(b23$AgeCat3.f,"label")<-labs[["AgeCat3.f"]]
attr(b23$AgeCat2.f,"label")<-labs[["AgeCat2.f"]]
attr(b23$hhdtypb4.f,"label")<-labs[["hhdtypb4.f"]]
attr(b23$dimarr4.f,"label")<-labs[["dimarr4.f"]]
attr(b23$edqual4.f,"label")<-labs[["edqual4.f"]]
attr(b23$wpdes4.f,"label")<-labs[["wpdes4.f"]]
attr(b23$VotRec0,"label")<-labs[["VotRec0"]]

levels(b23$nssec.f)<-c("Higher managerial","Higher professional","Lower P&M","Intermediate occupations",                                
                    "Small employers / own account", "Lower supervisory/technical","Semi-routine occupations",
                    "Routine occupations")
```

## 3. Univariates results

Results are presented as follows, under each tab below:
  
1.  Unweighted frequencies and proportions of the original variables, unrecoded
2.  Weighted frequencies and proportions of the recoded (ie missing/invalid values removed) variables

Please note that in the case of newly derived variable 1. and 2. will be identical 

::: {.panel-tabset}


```{r univariates}
#| results: asis
#| echo: false



b23.s<-svydesign(~1,weights=~wt,data=b23)

# Apply the function to all  variables 
#lapply(ivs, function(v) ufreq(v, b23))
rslt.u<-  lapply(vars, function(v) vfreq(v, b23))
rslt.r <- lapply(vars, function(v) wfreq2(v, b23.s) )
#rslt.c <- lapply(vars, wfreq.r)


# Print the tables for each dependent variable using kable for better formatting
for (i in 1:length(rslt.u)) {
  cat('### ', labs[[i]], '\n')
  
  cat(paste0("#### Unweighted frequency table of *",labs[i],"*", '\n'))
#  print(knitr::kable(rslt.u[[i]]),'html')
  print(rslt.u[[i]])
  cat('\n')
  
  cat(paste0("#### Weighted frequency table of *",labs[i],"*", '\n'))
  print(rslt.r[[i]])
  cat('\n')
  
  # cat(paste0("#### **Weighted frequency table of recoded *",labs[i],"* **", '\n'))
  # print(knitr::kable(rslt.c[[i]]),'html')
  # cat('\n')
  
}
cat('\n:::')
```


## 4. Bivariates results

This section contains contingency tables and Chi-Squared test of independence, for each variable listed below:
  
1. by voting behaviour at the 2019 GE 
2. by sex
3. by age, two categories
4. by age, three categories

All contingency tables were computed using weighted data.

::: {.panel-tabset}

```{r biv}
#| results: asis
#| echo: false


for (i in 1:length(ivars)) {
  
  cat('### ', labs[[i]], '\n')
  
  cat(paste0("#### Contingency table of  whether voted at the 2019 GE by *",labs[i],"* "))
  
  tmp.t<-svytable(as.formula(paste0("~VotGE19.f+", ivars[i])), b23.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
  rownames(tmp.p)<-c("",rownames(tmp.t))
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(
    tmp.p
  ),'html')
  
  cat('\n')
  
  t<-svychisq(as.formula(paste0("~", ivars[i],"+ VotGE19.f")), b23.s)
  
  print(t$method)
  cat('\n')
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  cat('\n')
  
  ################################################################################################
  
  
  if(ivars[i]!="gender.f"){
    
    cat(paste0("#### Contingency table of  Sex by *",labs[i],"*"))
    cat('\n')
    
    tmp.t<-svytable(as.formula(paste0("~", ivars[i],"+gender.f")), b23.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
    rownames(tmp.p)<-c("",rownames(tmp.t))
    names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
    
    print(kable(tmp.p))
    cat('\n')
    
    t<-svychisq(as.formula(paste0("~", ivars[i],"+ gender.f")), b23.s)
    
    print(t$method)
    cat('\n')
    print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
    
    cat('\n')
  }

if(ivars[i]!="AgeCat2.f"){
    
  cat(paste0("#### Contingency table of  Age (2 cat) by *",labs[i],"*"))
  cat('\n')
  
  tmp.t<-svytable(as.formula(paste0("~", ivars[i],"+AgeCat2.f")), b23.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
  rownames(tmp.p)<-c("",rownames(tmp.t))
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  t<-svychisq(as.formula(paste0("~", ivars[i],"+ AgeCat2.f")), b23.s)
  print(t$method)
  cat('\n')
  
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  cat('\n')
  }
  
  if(ivars[i]!="AgeCat3.f"){
    
  cat(paste0("#### **Contingency table of  Age (3 cat) by *",labs[i],"*"))
  cat('\n')
  tmp.t<-svytable(as.formula(paste0("~", ivars[i],"+AgeCat3.f")), b23.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
  rownames(tmp.p)<-c("",rownames(tmp.t))
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  t<-svychisq(as.formula(paste0("~", ivars[i],"+ AgeCat3.f")), b23.s)
  
  print(t$method)
  cat('\n')
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  
  cat('\n')
  }
}
cat('\n:::')
```


## 5. Further descriptives

This section presents:
  
  - Unweighted three way tables of age (two categories) and sex by whether voted at the 2019 general elections
  - Cross-sectional proportions of 50+ who cast their ballot at the GE, by election year, sex and age 

###  5.1 Whether voted at  the 2019 GE by gender and age bands

#### Sample description

```{r desc}
#| output: asis

print(kable(
  round((table(Age=b23$AgeCat2.f,Sex=b23$gender.f,"Voted"=b23$VotGE19.f))) 
),'html')
```

####  Weighted estimates:

- Women:
```{r descw}
#| output: asis

res<- svytable(~VotGE19.f+AgeCat2.f+gender.f,design = b23.s)

print(kable(
  rbind(
    rowPct(res[,,2]),
    c(100,100)
  )
)
)
```

- Men:
  
```{r descm}
#| output: asis

print(kable(
  rbind(
    rowPct(res[,,1]),
    c(100,100)
  )
)
)

```

### 5.2 Voting pattern by age, sex and general election


```{r plotge}
#| fig-width: 12
#| fig-height: 10

# for(ds in names(voted)) {
#   voted[[ds]]<-voted[[ds]] |>mutate(AgeCat3.f=as.factor(case_when(
#     indager>=50 & indager<70 ~ "50-69",
#     indager>=70 & indager<80 ~ "70-79",
#     indager>=80  ~ "80+"
#   )))
# }

results<-list()

for(ds in names(voted)) {
names(voted[[ds]])[which(substr(names(voted[[ds]]),1,5)=="VotGE")]<-"Wvot"
voted[[ds]]<- voted[[ds]] |>mutate(
  AgeCat3.f=
  as.factor(case_when(
  age>=50 & age<70 ~ "50-69",
  age>=70 & age<80 ~ "70-79",
  age>=80  ~ "80+"
)),
Wvot=as.numeric(Wvot)
)

}


des <- list(
  GE01 = svydesign(ids = ~1, weights = ~wt, data=voted[["GE01"]] |>filter(!is.na(wt))),
  GE05 = svydesign(ids = ~1, weights = ~wt, data=voted[["GE05"]] |>filter(!is.na(wt))),
  GE10 = svydesign(ids = ~1, weights = ~wt, data=voted[["GE10"]] |>filter(!is.na(wt))),
  GE15 = svydesign(ids = ~1, weights = ~wt, data=voted[["GE15"]] |>filter(!is.na(wt))),
  GE17 = svydesign(ids = ~1, weights = ~wt, data=voted[["GE17"]] |>filter(!is.na(wt))),
  GE19 = svydesign(ids = ~1, weights = ~wt, data=voted[["GE19"]] |>filter(!is.na(wt)))
)

for(ds in names(des)) {
  age_est <- svyby(~I(Wvot == 1 ), ~AgeCat3.f, des[[ds]], svymean, vartype = "ci", keep.var = TRUE,na.rm = T)
  names(age_est)[1]<-"Category"
  names(age_est)[c(3,5,7)]<-c("Proportion","CI_low","CI_up")
  
  #  age_est$Category <- "AGE"
  #  age_est$Level <- as.factor(age_est$AGE)
  age_est<-age_est|>select(Category,"Proportion","CI_low","CI_up"  )
  age_est$Dataset <- ds
  
  # Proportion by SEX
  sex_est <- svyby(~I(Wvot == 1), ~gender.f, des[[ds]], svymean, vartype = "ci", keep.var = TRUE,na.rm = T)
  names(sex_est)[1]<-"Category"
  names(sex_est)[c(3,5,7)]<-c("Proportion","CI_low","CI_up")
  sex_est<-sex_est|>select(Category,"Proportion","CI_low","CI_up"  )
  sex_est$Dataset <- ds
  
  # Combine
  results[[ds]] <- rbind(age_est, sex_est)
}  

plot_data <- bind_rows(results)
plot_data[,2:4]<-round(plot_data[,2:4]*100,1)
plot_data$Dataset<-as.factor(plot_data$Dataset)
levels(plot_data$Dataset)<-c(2001,2005,2010,2015,2017,2019)
# # Rename columns for ggplot
# plot_data <- plot_data |>
#   rename(Proportion = `I(Wvot == 1)TRUE`,
#          CI_low = `ci_l.I(Wvot == 1)TRUE`,
#          CI_high = `ci_u.I(Wvot == 1)TRUE`)

# Plotting
ggplot(plot_data, aes(x = Category, y = Proportion, group = Dataset)) +
  #  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_up), size=.9, width = 0.2) +
  geom_text(aes(label = Proportion), hjust = -.5, size = 4) +
  facet_wrap(~Dataset) +
  labs(title = "Proportion who voted at the last general election, by age and sex",
       x = "General Election Year",
       y = "Percent voted with 95% CIs",
       caption="Weighted cross-sectional estimates, BES Cross-sectional dataset") +
  theme_minimal() +
  theme(strip.text = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        plot.caption=element_text(hjust = 0),
        plot.title.size=element_text(size = 18))
```


## 6. Multivariate results

This section presents the results of four series of logistic regressions models of voting behaviour at the 2019 general elections:
  
1. Stepwise models including voting behaviour recorded at previous waves, and socio-economic characteristics
2. Stepwise models including  socio-economic characteristics only
3. Stepwise models including disability level, NS-SEC social class, whether religious, ethnicity and socio-economic characteristics
4. As 3. above,  alongside voting behaviour recorded at previous waves

All models were fitted using weights.

::: {.panel-tabset}


### 6.1 Models with socio-economic variables, including past voting behaviour
  
  
```{r multiv_w}
#| output: asis
b23.r<-b23 |>filter(!is.na(gender.f) & !is.na(AgeCat3.f) & !is.na(hhdtypb4.f) & !is.na(dimarr4.f) &
                    !is.na(edqual4.f)& !is.na(wpdes4.f) & !is.na(VotRec0) & !is.na(wt) & !is.na(VotGE19.f))

regw<-list()

regw[["a11"]]<-glm(VotGE19.f ~ VotRec0,
                   weights=wt,
                   b23.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.f ~ VotRec0+
                     gender.f,
                   weights=wt,
                   b23.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a13"]]<-glm(VotGE19.f ~ VotRec0+
                     gender.f+AgeCat3.f,
                   weights=wt,
                   b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a13a"]]<-glm(VotGE19.f ~ VotRec0+
                      gender.f+AgeCat3.f+hhdtypb4.f,
                    weights=wt,
                    b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a14"]]<-glm(VotGE19.f ~ VotRec0+
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f,
                   weights=wt, 
                   b23.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a15"]]<-glm(VotGE19.f ~ VotRec0+
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+
                     edqual4.f,  weights=wt,
                   b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


# regw[["a16"]]<-glm(VotGE19.f ~ VotRec0+
#                      gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+ edqual4.f+wpdes5.f, 
#                      weights=wt, b23.r,family=binomial())|>   
#                    tbl_regression(exponentiate = TRUE, digits=1) |> 
#                     add_glance_table(include=c(AIC,logLik,nobs)) |> 
#                     add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

tmp17<-glm(VotGE19.f ~ VotRec0+
             gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f,
           weights=wt, b23.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) 


regw[["a17"]]<- tmp17 |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



tmp18<-glm(VotGE19.f ~ VotRec0+
             gender.f*AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f,
           weights=wt, b23.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, digits=1, ci_method="wald") 
regw[["a18"]]<- tmp18 |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**"))


```
#### Coefficient plot of Models 7 & 8

```{r plot_w}
#| fig-width: 12
#| fig-height: 10

tmp17 |>plot()

tmp18 |>plot()
```



### 6.2 Models with socio-economic variables, without past voting behaviour
  

```{r multiv_w.w}
#| output: asis

b23.r<-b23 |>filter(!is.na(gender.f) & !is.na(AgeCat3.f) & !is.na(hhdtypb4.f) & !is.na(dimarr4.f) &
                          !is.na(edqual4.f)& !is.na(wpdes4.f)  & !is.na(wt) & !is.na(VotGE19.f )) 

regw<-list()

regw[["a12"]]<-glm(VotGE19.f ~ 
                     gender.f,
                   weights=wt,
                   b23.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.f ~ 
                     gender.f+AgeCat3.f,
                   weights=wt,
                   b23.r,family=binomial())|>                   
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13a"]]<-glm(VotGE19.f ~ 
                      gender.f+AgeCat3.f+hhdtypb4.f,
                    weights=wt,
                    b23.r,family=binomial())|>                  
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a14"]]<-glm(VotGE19.f ~ 
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f,
                   weights=wt,
                   b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.f ~ 
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+
                     edqual4.f,
                   weights=wt,
                   b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



# regw[["a16"]]<-glm(VotGE19.f ~
#                      gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+
#                      edqual4.f+wpdes4.f,
#                    weights=wt,
#                    b23.r,family=binomial())|>   
#                     tbl_regression(exponentiate = TRUE, digits=1) |>                   
#                     add_glance_table(include=c(AIC,logLik,nobs)) |> 
#                     add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.f ~ 
             gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+
             edqual4.f+wpdes4.f,
           weights=wt,
           b23.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE, digits=1) 



regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp18<-glm(VotGE19.f ~ 
             gender.f*AgeCat3.f+hhdtypb4.f+dimarr4.f+
             edqual4.f+wpdes4.f,
           weights=wt,
           b23.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, digits=1) 

regw[["a18"]] <- tmp18 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**","**M6**", "**M7**"))

```

#### Coefficients plot of Models 7 & 8

```{r plot_w.w}
#| fig-width: 12
#| fig-height: 10

tmp17 |>plot()

tmp18 |>plot()

```


### 6.3 Models with extra covariates, no past voting behaviour

```{r extrav}
#| output: asis

b23.r<-b23 |>filter(!is.na(gender.f) & !is.na(AgeCat3.f) & !is.na(hhdtypb4.f) & !is.na(dimarr4.f) &
                          !is.na(edqual4.f)& !is.na(wpdes4.f) & !is.na(disab.f) &
                          !is.na(relig.f)& !is.na(nssec.f)& !is.na(ethnic.f) & !is.na(wt) & !is.na(VotGE19.f ))


regw<-list()


regw[["a11"]]<-glm((VotGE19.f) ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
                     disab.f,
                   weights=wt,b23.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = disab.f) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)


regw[["a12"]]<-glm(VotGE19.f ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f
                   +disab.f+ethnic.f,
                   weights=wt, b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = c("disab.f","ethnic.f")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)


regw[["a13"]]<-glm(VotGE19.f ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
                     +disab.f+ethnic.f+relig.f,
                   weights=wt, b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = c("disab.f","ethnic.f", "relig.f")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)



tmp14<-glm(VotGE19.f ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
                     +disab.f+ethnic.f+relig.f+nssec.f,
                   weights=wt,b23.r,family=binomial())|>
  tbl_regression(exponentiate = T,
                 digits=1,
                 include = c("disab.f","ethnic.f", "relig.f", "nssec.f")) 

regw[["a14"]]<-tmp14|>  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**"))
```

#### Coefficients plot of Model 4

```{r plot_extrav}
#| fig-width: 12
#| fig-height: 10
tmp14 |>plot()
```


### 6.4 Models with extra covariates, including past voting behaviour


```{r lastreg}
b23.r<-b23 |>filter(!is.na(gender.f) & !is.na(AgeCat3.f) & !is.na(hhdtypb4.f) & !is.na(dimarr4.f) &
                      !is.na(edqual4.f)& !is.na(wpdes4.f) & !is.na(disab.f) &
                      !is.na(relig.f)& !is.na(nssec.f)& !is.na(ethnic.f) & !is.na(wt) & !is.na(VotGE19.f ))


regw<-list()


regw[["a11"]]<-glm((VotGE19.f) ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
                     disab.f,
                   weights=wt,b23.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = disab.f) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)


regw[["a12"]]<-glm(VotGE19.f ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f
                   +disab.f+ethnic.f,
                   weights=wt, b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = c("disab.f","ethnic.f")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)


regw[["a13"]]<-glm(VotGE19.f ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
                     +disab.f+ethnic.f+relig.f,
                   weights=wt, b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = c("disab.f","ethnic.f", "relig.f")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)

regw[["a14"]]<-glm(VotGE19.f ~
                     gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
                     +disab.f+ethnic.f+relig.f +nssec.f,
                   weights=wt, b23.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE,
                 digits=1,
                 include = c("disab.f","ethnic.f", "relig.f", "nssec.f")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)


tmp15<-glm(VotGE19.f ~
             gender.f+AgeCat3.f+hhdtypb4.f+dimarr4.f+edqual4.f+wpdes4.f+
             +disab.f+ethnic.f+relig.f+nssec.f +VotRec0,
           weights=wt,b23.r,family=binomial())|>
  tbl_regression(exponentiate = T,
                 digits=1,
                 include = c("disab.f","ethnic.f", "relig.f", "nssec.f", "VotRec0")) 

regw[["a15"]]<-tmp15|>  add_glance_table(include=c(AIC,logLik,nobs)) |>
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T)




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**"))
```

#### Coefficients plot of Model 4

```{r plot_extrav2}
#| fig-width: 12
#| fig-height: 10
tmp15 |>plot()

```


:::

  