---
title: "ELSA voting patterns study"
subtitle: Exploratory analysis  - draft version 4
author: "Pierre Walthéry"
date: today
date-format: DD MMMM YYYY
format: 
  html:
   embed-resources: true
   page-layout: full
   mainfont: "Open Sans"
   toc: true
   smooth-scroll: true
   toc-location: left

#  odt: default
execute:
  warning: false
  message: false
  echo: false
  cache: false

---

## Introduction
This document presents preliminary descriptive,  uni-, bi-   and multivariate analysis   of voting at the 2019 General Elections  among the 50+, using  data from the English Longitudinal Study of Ageing - ELSA at Wave 10.

- Section 1 presents the variables included in the analysis
- Section 2 contains information about variable recoding and related issues
- Section 3 includes systematic unweighted and weighted univariate frequency tables
- Section 4 documents systematic unweighted and weighted contingency tables of the variables included in the analysis by turnout at the 2019 general elections, age, sex. 
- Section 5 presents additional three way analysis of voting behaviour by age, sex and the year general elections took place.
- Section 6 presents the results of four series of stepwise logistic regression models of voting at the 2019 GE.



```{r data}

rm(list=ls())

library(haven)
library(survey)
library(dplyr)
library(knitr)
library(gtsummary)
library(ggplot2)

datadir<-"~/Data/elsa/UKDA-5050-stata/stata/stata13_se/"

# elsa0<-read_dta(paste0(datadir,"wave_0_common_variables_v2.dta"))
# elsa.ifs<-read_dta(paste0(datadir,"wave_10_ifs_derived_variables.dta"))
# elsa1<-read_dta(paste0(datadir,"wave_1_core_data_v3.dta")) |> select(idauniq,scptpa1,indager,indsex,w1wgt)
# elsa3<-read_dta(paste0(datadir,"wave_3_elsa_data_v4.dta"))  |> select(idauniq,scpt01,indager,indsex,w3xwgt)
# elsa8<-read_dta(paste0(datadir,"wave_8_elsa_data_eul_v2.dta")) |> select(idauniq,scptrvt, indager,indsex,w8xwgt)
# elsa9<-read_dta(paste0(datadir,"wave_9_elsa_data_eul_v2.dta")) |> select(idauniq,scptrvt,indager,indsex,w9xwgt)
# elsa10<-read_dta(paste0(datadir,"wave_10_elsa_data_eul_v4.dta"))
# 
# voted<-list(
# GE01=elsa1,
# GE05=elsa3,
# GE15=elsa8,
# GE17=elsa9,
# GE19=elsa10 |> select(idauniq,scsptrvt,indager,indsex,w10xwgt)
# )
# 
# names(voted[["GE01"]])[which(names(voted[["GE01"]])=="scptpa1")]<-"Wvot"
# names(voted[["GE05"]])[which(names(voted[["GE05"]])=="scpt01")]<-"Wvot"
# names(voted[["GE15"]])[which(names(voted[["GE15"]])=="scptrvt")]<-"Wvot"
# names(voted[["GE17"]])[which(names(voted[["GE17"]])=="scptrvt")]<-"Wvot"
# names(voted[["GE19"]])[which(names(voted[["GE19"]])=="scsptrvt")]<-"Wvot"
# 
# 
# names(elsa1)[which(names(elsa1)=="scptpa1")]<-"VotGE01"
# names(elsa3)[which(names(elsa3)=="scpt01")]<-"VotGE05"
# names(elsa8)[which(names(elsa8)=="scptrvt")]<-"VotGE15"
# names(elsa9)[which(names(elsa9)=="scptrvt")]<-"VotGE17"
# 
# for(w in c(1,3,8,9)){
# tmp<-eval(parse(text=paste0("elsa",w)))
# names(tmp)[3:4]<-c(paste0("indager",w),paste0("indsex",w))
# eval(parse(text=paste0("elsa",w,"<-tmp")))
# }
# 
# elsaw<-merge(elsa10,elsa0|>
#                  select(idauniq,hhdtypb,tenureb,ethnic),
#                  by="idauniq",all.x=T,all.Y=F)
# 
# elsaw<-merge(elsaw,elsa.ifs|>
#                  select(idauniq,edqual),
#                  by="idauniq",all.x=T,all.Y=F)
# 
# ### Cross-sectional voting subsamples
# vot1389<-merge(
#      merge(elsa1,
#            elsa3,
#                  by="idauniq",all=T
#            ),
#       merge(elsa8 ,
#             elsa9 ,
#                  by="idauniq",all=T
#            ),
#            by="idauniq",all=T)
# 
# 
# vot13890<-merge(vot1389,elsa10 |> select(idauniq,scsptrvt,indager,indsex,w10xwgt) ,
#              by="idauniq",all=T
#            )
# 
# names(vot13890)[which(names(vot13890)=="scsptrvt")]<-"VotGE19"
# names(vot13890)[which(names(vot13890)=="indager")]<-"indager10"
# names(vot13890)[which(names(vot13890)=="indsex")]<-"indsex10"
# 
# names(elsaw)[which(names(elsaw)=="scsptrvt")]<-"VotGE19"
# 
# 
# elsaw<-merge(elsaw, vot1389,
#              by="idauniq",all=T
#            )
# 
# 
# elsaw<-elsaw|>filter(!is.na(w10xwgt)) |>
#            select(idauniq,all_of(ivs),exlo80, psagf, exrslf, indager, VotGE19,w10xwgt)
# 
# # Save the list to an RDS file
# saveRDS(voted, file = "/home/mscsepw2/Dropbox/work/ELSAwork/data/voted.rds")
# 
# write_dta(vot13890, "/home/mscsepw2/Dropbox/work/ELSAwork/data/elsal.dta")
# write_dta(elsaw, "/home/mscsepw2/Dropbox/work/ELSAwork/data/elsaw.dta")

elsaw<-read_dta("/home/mscsepw2/Dropbox/work/ELSAwork/data/elsaw.dta")
elsal<-read_dta("/home/mscsepw2/Dropbox/work/ELSAwork/data/elsal.dta")
voted <- readRDS("/home/mscsepw2/Dropbox/work/ELSAwork/data/voted.rds")

###############################################################################################################
```

```{r functions,tidy=T}
source("functions.R")
```



```{r recode}
############################################################################################
## Renaming voting variables
#elsaw$VotGE19<-elsaw$scsptrvt

avars<-c("AgeCat2.fr", "AgeCat3.fr","cfmap", "cfmetm", "dimarr", "edqual", "erfvol", "ethnic", "exrela", "headlba","headlbe","hehelf", "hhdtypb","hobb","iafcon", "iafind","indsex", "pscedd", "pscede", "scorgpo","scorgrl","spcar",  "sptraa", "tenureb","VotGE01","VotGE05","VotGE15","VotGE17","VotGE19","VotRec0","VotRec01","w10nssec5","wpdes")    

ovars<-c("cfmap", "cfmetm", "dimarr", "edqual", "erfvol", "ethnic", "exrela", "headlba","headlbe","hehelf", "hhdtypb","hobb","iafcon", "iafind","indsex", "pscedd", "pscede", "scorgpo","scorgrl","spcar",  "sptraa", "tenureb", "VotGE01","VotGE05","VotGE15","VotGE17","VotGE19","w10nssec5","wpdes")    


wvars<-c("erfvol", "ethnic", "headlba","headlbe", "hobb", "iafind","indsex", "pscedd", "pscede", "scorgpo","scorgrl", "spcar",  "VotGE01","VotGE05","VotGE15","VotGE17","VotGE19")    


dvars<-c("AgeCat2.fr", "AgeCat3.fr","VotRec0.fr","VotRec01.fr")

uvars<-paste0(ovars,".f")
rvars<-paste0(ovars,".fr")

bivars19<-c("AgeCat2","AgeCat3", "cfmap", "cfmetm", "dimarr", "edqual", "erfvol", "ethnic", "exrela", "headlba","headlbe","hehelf", "hhdtypb","hobb","iafcon", "iafind","indsex", "pscedd", "pscede", "scorgpo","scorgrl","spcar",  "sptraa", "tenureb","VotGE01","VotGE05","VotGE15","VotGE17","VotRec0","VotRec01","w10nssec5","wpdes")     


labs<-list(
cfmap.f="Self-rated mental abilities",
cfmetm.f="Self-rated memory",
dimarr.f="Marital/relationship status",
edqual.f="Educational level",
erfvol.f="Volunteered",
ethnic.f="White vs Non-white",
exrela.f="Too little money to spend on their needs?",
headlba.f="Difficulty bathing or showering",
headlbe.f="Difficulty getting in and out of bed",
hehelf.f="Self-reported general health",
hhdtypb.f="Recoded household type, 4 categories",
hobb.f="Internet connection?",
iafcon.f="Financial situation",
iafind.f="Who has the final say in big financial decisions",
indsex.f="Sex",
pscedd.f="Whether happy much of the time last  week",
pscede.f="Feels lonely?",
scorgpo.f="Whether member of a political party, trade union or environmental groups",
scorgrl.f="Whether member of a church or other religious group",
spcar.f="Whether has use of car/van, as a driver or a passenger",
sptraa.f="How often respondent uses public transport",
tenureb.f="Household Tenure",
VotGE01.f="Whether voter at the 2001 GE",
VotGE05.f="Whether voter at the 2005 GE",
VotGE15.f="Whether voter at the 2015 GE",
VotGE17.f="Whether voter at the 2017 GE",
VotGE19.f="Whether voter at the 2017 GE",
w10nssec5.f="NS-SEC 5 category",
wpdes.f="Economic activity",
AgeCat2.fr="Recoded age, 2 category",
AgeCat3.fr="Recoded age, 3 category",
VotRec0.fr="Past voting record, v1",
VotRec01.fr="Past voting record, v2"
)



## Recode

elsaw<-elsaw|>mutate(
  # AgeCat85.fr=as.factor(case_when(
  #   indager>=50 & indager<65 ~ "50-64",
  #   indager>=65 & indager<75 ~ "65-74",
  #   indager>=75 & indager<85 ~ "75-84",
  #   indager>=85  ~ "85+"
  # )),
  # AgeCat80.fr=as.ordered(case_when(
  #   indager>=50 & indager<65 ~ "50-64",
  #   indager>=65 & indager<70 ~ "65-69",
  #   indager>=70 & indager<75 ~ "70-74",
  #   indager>=75 & indager<80 ~ "75-79",
  #   indager>=80  ~ "80+"
  # )),
  AgeCat2.fr=as.ordered(case_when(
    indager>=50 & indager<70 ~ "50-69",
    indager>=70 ~ "70+"
  )),
  AgeCat3.fr=as.ordered(case_when(
    indager>=50 & indager<70 ~ "50-69",
    indager>=70 & indager<80 ~ "70-79",
    indager>=80  ~ "80+"
  )),
    cfmap.f=as.ordered(case_when(
    cfmap==1 | cfmap==2 ~ "Excellent/v good",
    cfmap==3 ~ "Good",
    cfmap==4 | cfmap==5 ~ "Fair/poor",
.default = NA
  )),
    cfmetm.f=as.ordered(case_when(
    cfmetm==1 | cfmetm==2 ~ "Excellent/v good",
    cfmetm==3 ~ "Good",
    cfmetm==4 | cfmetm==5 ~ "Fair/poor",
.default = NA
  )),
  dimarr.f=as.ordered(case_when(
    dimarr==1  ~ "Single",
    dimarr==2 | dimarr==3 ~ "Married/SP",
    dimarr==4 | dimarr==5 ~ "Divorced/separated",
    dimarr==6 ~ "Widowed"
  )),
  edqual.f=as.ordered(case_when(
    edqual==1 | edqual==2 ~ "Tertiary",
    edqual==3 | edqual==4  | edqual==5 ~ "Secondary",
    edqual==6 ~ "Foreign",
    edqual==7 ~ "No qualifications"
  )),
  exrela.f=as.ordered(case_when(
    exrela==1 |     exrela==2  ~ "Never/rarely",
    exrela==3 ~ "Sometimes",
    exrela==4 | exrela==5 ~ "Often/M of the T"
  )),
  hehelf.f=as.ordered(case_when(
    hehelf==1  | hehelf==2 ~ "Excel/V good",
    hehelf==3 ~ "Good",
    hehelf==4 | hehelf==5  ~ "Fair/poor"
  )),
  hhdtypb.f=as.ordered(case_when(
    hhdtypb==1  | hhdtypb==7 ~ "Single person HH",
    hhdtypb==2 | dimarr==6 ~ "Two adults HH",
    hhdtypb==3 | dimarr==4 ~ "Family, large or small ",
    hhdtypb==5 ~ "Large adult HH",
    .default = "Other"
  )),
    iafcon.f=as.ordered(case_when(
    iafcon==1   ~ "Manage very well",
    iafcon==2   ~ "Manage quite well",
    iafcon==3   ~ "Get by alright",
    iafcon==4 | iafcon==5 | iafcon==6 ~ "Does not manage well"
  )),
    sptraa.f=as.ordered(case_when(
    sptraa==1 | sptraa==2  ~ "MT once a week",
    sptraa==3 | sptraa==4     ~ "MT once a month",
    sptraa==5 | sptraa==6  ~ "Monthly or less"
  )),
   tenureb.f=as.ordered(case_when(
   tenureb==1   ~ "Owner",
   tenureb==2 | tenureb==3 ~ "Mortgage",
   tenureb==4 |tenureb==5  ~ "Renter"
  )),
   w10nssec5.f=as.ordered(case_when(
   w10nssec5==1   ~ "Higher MAP",
   w10nssec5==2  ~ "Intermediate",
  w10nssec5==3 | w10nssec5==4  ~ "Small emp, lower superv.",
    w10nssec5==5  ~ "Semi-routine/routine"
  )),

  wpdes.f=as.ordered(case_when(
    wpdes==1 | wpdes==96 ~ "Retired (inc part)",
    wpdes==2 | wpdes==3~ "In employment",
    wpdes==4 | wpdes==6~ "FT carer + unemp.",
    wpdes==5 ~ "LT sick/disabled"
  ))            

)            



#### Voting record - 2001-2017 
for(l in c("VotGE01","VotGE05","VotGE15","VotGE17")){
  tmp<-as.numeric(
       eval(
         parse(
           text=paste0("elsaw$",l)
           )
         )
       )

    elsaw[paste0(l,".n")]<-ifelse(tmp<0 | is.na(tmp),0,tmp)  
}

### Raw GE voting number
elsaw$votrec<-elsaw$VotGE01.n+elsaw$VotGE05.n+elsaw$VotGE15.n+elsaw$VotGE17.n

### Factor version, 3 cat 
elsaw<-elsaw|>mutate(VotRec0.fr=as.factor(case_when(
  votrec==0 ~ "None", 
  votrec==1 | votrec==2 ~ "1-2",
  votrec==3 | votrec==4 ~ "3-4")),
    VotRec01.fr=as.factor(case_when(
    votrec==0 | votrec==1~ "None or 1", 
    votrec==2 ~ "2",
    votrec==3 | votrec==4 ~ "3-4")
) )

```



```{r factor}
### Removing vars already created

for (hav in wvars  ) {
    elsaw<-cbind(elsaw,tmp=tfactor(
    eval(
      parse(
        text=paste0("elsaw$",hav)))))

names(elsaw)[ncol(elsaw)]<-paste0(hav,".f")
  }

```



```{r miscrec}
for(v  in ovars) {
nv<-paste0(v,".fr")
ov<-paste0(v,".f")
  elsaw<-elsaw|>mutate(nv=
          eval(
      parse(
        text=paste0(  
          "as.factor(case_when(",
          ov,"==\"[-9] Refusal (8)\"       ~ NA_character_,",
          ov,"==\"[-8] Don\'t know (9)\"                              ~ NA_character_,",
          ov,"==\"[-8] Don\'t know\"                                  ~ NA_character_,",
          ov,"==\"[-8] don\'t know\"                                 ~ NA_character_,",
          ov,"==\"[-9] Refused\"                                      ~ NA_character_,",
          ov,"==\"[-9] Refusal\"      ~ NA_character_,",
          ov,"==\"[-9] refusal\"      ~ NA_character_,",
          ov,"==\"[96] SPONTANEOUS: Semi-retired\"                    ~ NA_character_,",
          ov,"==\"[86] Irrelevant answer - not codeable 01-06 or 96\" ~ NA_character_,",
          ov,"==\"[85] Other answer - not codeable 01-06 or 96\"      ~ NA_character_,",
          ov,"==\"[6] SPONTANEOUS - do not currently use\"      ~ NA_character_,",
          ov,"==\"[85] Other answer - not codeable 01-04\"      ~ NA_character_,",
          ov,"==\"[-2] Self-completion instrument not completed\"      ~ NA_character_,",
          ov,"==\"[-1] Item not applicable\"      ~ NA_character_,",
          ov,"==\"[-1] Item not applicable\"                               ~ NA_character_,",
          ov,"==\"[-1] Not applicable\"                               ~ NA_character_,",
          ov,"==\"[-9] Not answered (99)\"      ~ NA_character_,",
          ov,"==\"[-9] Not answered\"      ~ NA_character_,",
          ov,"==\"[-3] No valid answer\"      ~ NA_character_,",
          ov,"==\"[99] Other\"      ~ NA_character_,",
          ov,"==\"[-2] not asked\"      ~ NA_character_,",
          ov,"==\"[-3] Incomplete/No job info collected\"      ~ NA_character_,",
          ov,"==\"[-9] No answer/refused\"      ~ NA_character_,",
          ".default =",ov,"))"
        )
      )
    ))
  
names(elsaw)[ncol(elsaw)]<-paste0(v,".fr")
}

levels(elsaw$VotGE19.fr)[c(1,2)]<-c("Didn't vote","Voted")
levels(elsaw$VotGE17.fr)[c(1,2)]<-c("Didn't vote","Voted")
levels(elsaw$VotGE15.fr)[c(1,2)]<-c("Didn't vote","Voted")
levels(elsaw$VotGE05.fr)[c(1,2)]<-c("Didn't vote","Voted")
levels(elsaw$VotGE01.fr)[c(1,2)]<-c("Didn't vote","Voted")





for(vr in names(labs)){                        ### Leaving AgeCaat out
  attr(elsaw[vr],"label")<-labs[[vr]]
  
  # if(vr!="VotRec0.fr" & vr!="VotRec01.fr"){
  # attr(elsaw[paste0(vr,"r")],"label")<-labs[[vr]]
  # }
}


### Missing labels
levels(elsaw$scorgpo.fr)<-c("No", "Yes")
levels(elsaw$scorgrl.fr)<-c("No", "Yes")

``` 



## 1. Variables included

|Name|Description|Variable label
|----|-----------|------------------------------------:
Age  2 categories  | AgeCat2    | `{r} attr(elsaw$AgeCat80, "label")`
Age 3 categories  | AgeCat3    | `{r} attr(elsaw$AgeCat85, "label")`
Sex  | INDSEX    | `{r} attr(elsaw$indsex, "label")`
Marital status|DIMARR |`{r} attr(elsaw$dimarr, "label")`
Household type| hhdtypb|`{r} attr(elsaw$hhdtypb, "label")`
Social class – NS-SEC | W10NSSEC5|`{r} attr(elsaw$w10nssec5, "label")`
Main economic activity| WPDES|`{r} attr(elsaw$wpdes, "label")`
Education/highest qualification| EDQUAL|`{r} attr(elsaw$edqual, "label")`
Ethnicity | ETHNIC|`{r} attr(elsaw$ethnic, "label")`
Religion | SCORGRL|`{r} attr(elsaw$scorgrl, "label")`
General Health| HEHELF|`{r} attr(elsaw$hehelf, "label")`
Mental Health| CFMAP |`{r} attr(elsaw$cfmap, "label")`
Memory issues| CFMETM|`{r}  attr(elsaw$cfmetm, "label")`
Past voting behaviour|VotGE1,VotGE3,VotGE8,VotGE9|Voted in  past GE  (from previous waves 1, 3, 8, 9, 10)`
Voted at the 2019 GE|SCSPTRVT|`{r}  attr(elsaw$scsptrvt, "label")`
Capacity everyday activities|HEADLB|`{r}  attr(elsaw$headlb, "label")`
Financial security|IAFCON,IAFINS,EXRELA|`{r}  attr(elsaw$ervol, "label")`
Control|IAFIND|`{r}  attr(elsaw$iafind, "label")`
Financial future | EXRSLF|`{r}  attr(elsaw$exrslf, "label")`
Happiness | PSCEDD|`{r}  attr(elsaw$pscedd, "label")`
Age perception | PSAGF|`{r}  attr(elsaw$psagf, "label")`
Social isolation | PSCEDE|`{r}  attr(elsaw$pscede, "label")`
Use of car | SPCAR|`{r}  attr(elsaw$spcar, "label")`
Use of public transport | SPTRAA|`{r}  attr(elsaw$sptraa, "label")`
Lift from friends | SPLIFT|`{r}  attr(elsaw$splift, "label")`
Grandchildren|DIGRAN |`{r}  attr(elsaw$digran, "label")`
Internet use | HOBB|`{r}  attr(elsaw$hobb, "label")`
Life expectancy expectation | EXLO80|`{r}  attr(elsaw$exlo80, "label")`
Volunteering | ERFVOL|`{r}  attr(elsaw$erfvol, "label")`
Caring responsibility| |`{r}  attr(elsaw$ervol, "label")`
Civic engagement|SCORGPO|`{r}  attr(elsaw$scorgpo, "label")`
Weights |w10xwgt | Wave 10 cross-sectional weight"                                                   


<!-- Weights | w10w1lwgt | Wave 10 Longitudinal weight (wave 1 base)"                                       -->
<!-- Weights | w10w4lwgt | Wave 10 Longitudinal weight (wave 4 base)"                                       -->
<!-- Weights |w10scwt | Wave 10 main self-completion weight"   -->
<!-- - Other activities: WPACT -->
  
  
## 2. Variables recoding 
  
### Recoding schemes:
  
1. Household type (HHDTYPB):
  
  - Single person (adult) households 
  - Families (large + small)
  - 2 adults households
  - Large adults HH


2. Marital status (DIMARR)

  - Single/never married
  - Married
  - Separated/dicvorced/widowed

3. Employment status (WPDES)

  - Retired + looking after family/home
  - In employment 
  -  Long term sick + unemployed

4. Highest qualification (EDQUAL)

  - Detailed version
  
    - Degree or equivalent 
    - Higher ed below degree
    - A level or equivalent
    - GCSE or equivalent
    - Foreign
    - No qualification

  - Short version
  
    - Higher education 
    - Secondary education
    - Foreign
    - No qualification


|Name|Fieldwork|Sample|Of which core|Vote asked|Last GE
|----|---------|-----------|-------|------|-------:
  Wave 1 | 2002-03 | 12,100|11,391|Yes|June 2001 
Wave 2 |2004/05 |9,432|8,780|No|June 2001
Wave 3 |2006/07 |9,771|8,810|Yes|May 2005
Wave 4 |2008/09 |11,050|9,886|No|May 2005
Wave 5 |2010/11 | 10,274|9,090|No|May 2010
Wave 6 |2012/13 |10,601|9,169|No|May 2010
Wave 7 |2014/15 |9,666,|8,249|No|May 2010
Wave 8 |2016/17 |8,445| 7,223|Yes|May 2015
Wave 9|2018/19 |8,736| 7,289|Yes|June 2017
Wave 10|2021-23|-|-|Yes|Dec. 2019
:Table 1: *ELSA fieldwork dates*
  Source: ELSA Wave 9 report, Table 1.1; Wikipedia.


#### Recoding notes and issues

- There is potentially a large drop in the number of  obsersations resulting from  combining the voting records across waves: `{r} prettyNum(length(!is.na(elsaw$VotGE19)[!is.na(elsaw$VotGE01) | !is.na(elsaw$VotGE05) | !is.na(elsaw$VotGE15) | !is.na(elsaw$VotGE15)]),big.mark = ",")`. For this reason, missing values were coded as 0. As a result there may be a need to add a control for British vs non British citizenship. 
- Ethnic has `{r} prettyNum(table(is.na(elsaw$ethnic))[2],big.mark = ",")` missing values. I do not recommend using it.


## 3. Univariates results

Results are presented as follows, under each tab below:
  
  1.  Unweighted frequencies and proportions of the original variables, unrecoded
  2.  Weighted frequencies and proportions of the recoded (ie missing/invalid values removed) variables

Please note that in the case of newly derived variable 1. and 2. will be identical 



::: {.panel-tabset}


```{r univariates}
#| results: asis
#| echo: false




elsaw.s<-svydesign(~1,weights=~w10xwgt,data=elsaw)

# Apply the function to all  variables 

rslt.u<-  lapply(c(uvars,dvars), function(v) vfreq(v, elsaw))

rslt.r <- lapply(c(rvars,dvars), function(v) wfreq2(v, elsaw.s) )



# Print the tables for each dependent variable using kable for better formatting
for (i in 1:length(rslt.u)) {
   cat('### ', labs[[i]], '\n')
  
    cat(paste0("#### **Unweighted frequency table of unrecoded *",c(uvars,dvars)[i],"* **", '\n'))
    print(rslt.u[[i]])
    cat('\n')
    

    cat(paste0("#### **Weighted frequency table of recoded *", c(rvars,dvars)[i],"* **", '\n'))
    print(rslt.r[[i]])
    cat('\n')

    }
cat('\n:::')
```




## 4. Bivariates results

This section contains for each variable used in the study, the following contingency tables:

  1. With voter turnout at the 2019 General Election
  2. With sex
  4. With age, two and three categories

All contingency tables were computed with weighted data and include  $\chi^2$ test of independence.


### **1. Voter turnout at the 2019 GE **


::: {.panel-tabset}

```{r biv}
#| results: asis
#| echo: false


for (v in bivars19) {
  
   cat('#### ', labs[[paste0(v,".f")]], '\n')
 
  cat(paste0("##### *Whether voted at 2019 GE by ",labs[[paste0(v,".f")]],"(",v, ")*"))

  tmp.t<-svytable(as.formula(paste0("~VotGE19.fr + ", v,".fr")), elsaw.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(
    tmp.p
  ),'html')
  
  cat('\n')
  
  t<-svychisq(as.formula(paste0("~", v,".fr","+ VotGE19.fr")), elsaw.s)
  
  print(t$method)
  cat('\n')
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  cat('\n')
  
  ################################################################################################
  
}

cat('\n:::')

```




### **2. Sex **

::: {.panel-tabset}

```{r bisex}
#| results: asis
#| echo: false

for (v in bivars19) {
  
  if(v!="indsex"){
     ttl<-labs[[paste0(v,".f")]]

       if(v=="Agecat2" | v=="Agecat3"){
     ttl<-labs[[paste0(v,".fr")]]
       }
     
   cat('#### ', labs[[paste0(v,".f")]], '\n')
 
    cat(paste0("##### *Sex by ",labs[[paste0(v,".f")]],"(",v, ")*"))

    
    tmp.t<-svytable(as.formula(paste0("~indsex.fr + ", v,".fr")), elsaw.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
    
    print(kable(tmp.p))
    cat('\n')
    
    t<-svychisq(as.formula(paste0("~", v,".fr","+ indsex.fr")), elsaw.s)
    
    print(t$method)
    cat('\n')
    print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
    
  cat('\n')
  
  ################################################################################################
  }
}

cat('\n:::')

```

  
### **3. Age, 2 & 3 categories **

::: {.panel-tabset}

```{r age}
#| results: asis
#| echo: false

for (v in bivars19) {
  
  if(v!="AgeCat2" & v!="AgeCat3"){
  
  
   cat('#### ', labs[[paste0(v,".f")]], '\n')
 
    cat(paste0("##### *Age 2 category by ",labs[[paste0(v,".f")]],"(",v, ")*"))
  
  tmp.t<-svytable(as.formula(paste0("~AgeCat2.fr +", v,".fr")), elsaw.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  t<-svychisq(as.formula(paste0("~", v,".fr","+ AgeCat2.fr")), elsaw.s)
  print(t$method)
  cat('\n')
  
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  cat('\n')
  
    cat(paste0("##### *Age 3 category by ",labs[[paste0(v,".f")]],"(",v, ")*"))
  cat('\n')
  tmp.t<-svytable(as.formula(paste0("~AgeCat3.fr + ", v,".fr")), elsaw.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p,colSums(tmp.p))
  rownames(tmp.p)<-c("",rownames(tmp.t),"Total")
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  t<-svychisq(as.formula(paste0("~", v,".fr","+ AgeCat3.fr")), elsaw.s)
  
  print(t$method)
  cat('\n')
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  
  cat('\n')
  }
}
cat('\n:::')
```




## 5. Further descriptives
  
This section presents:

- Unweighted three way tables of age (two categories) and sex by whether voted at the 2019 general elections

- Cross-sectional proportions of 50+ who cast their ballot at the GE, by election year, sex and age 

###  5.1 Whether voted at  the 2019 GE by gender and age bands

#### Sample description

```{r desc}
#| output: asis

print(kable(
round((table(Age=elsaw$AgeCat2.fr,Sex=elsaw$indsex.fr, "Voted"=elsaw$VotGE19.fr))) 
),'html')
```

####  Weighted estimates:

- Women:
```{r descw}
#| output: asis

print(kable(
rbind(
    rowPct(svytable(~VotGE19.fr+AgeCat2.fr+indsex.fr,design = elsaw.s)[,,2]),
    c(100,100)
    )
)
)
```

- Men:

```{r descm}
#| output: asis

print(kable(
rbind(
rowPct(svytable(~VotGE19.fr+AgeCat2.fr+indsex.fr,design = elsaw.s)[,,1]),
    c(100,100)
    )
)
)
```

### 5.2 Voting pattern by age, sex and general election


```{r plotge}
#| fig-width: 12
#| fig-height: 10

for(ds in names(voted)) {
  voted[[ds]]<-voted[[ds]] |>mutate(AgeCat3.f=as.factor(case_when(
    indager>=50 & indager<70 ~ "50-69",
    indager>=70 & indager<80 ~ "70-79",
    indager>=80  ~ "80+"
  )))
}

results<-list()
des <- list(
  GE01 = svydesign(ids = ~1, weights = ~w1wgt, data=voted[["GE01"]] |>filter(!is.na(w1wgt))),
  GE05 = svydesign(ids = ~1, weights = ~w3xwgt, data=voted[["GE05"]] |>filter(!is.na(w3xwgt))),
  GE15 = svydesign(ids = ~1, weights = ~w8xwgt, data=voted[["GE15"]] |>filter(!is.na(w8xwgt))),
  GE17 = svydesign(ids = ~1, weights = ~w9xwgt, data=voted[["GE17"]] |>filter(!is.na(w9xwgt))),
  GE19 = svydesign(ids = ~1, weights = ~w10xwgt, data=voted[["GE19"]] |>filter(!is.na(w10xwgt)))
)

for(ds in names(des)) {
  age_est <- svyby(~I(Wvot == 1), ~AgeCat3.f, des[[ds]], svymean, vartype = "ci", keep.var = TRUE)
  names(age_est)[1]<-"Category"
  #  age_est$Category <- "AGE"
  #  age_est$Level <- as.factor(age_est$AGE)
  age_est<-age_est|>select(Category,"I(Wvot == 1)TRUE","ci_l.I(Wvot == 1)TRUE","ci_u.I(Wvot == 1)TRUE"  )
  age_est$Dataset <- ds
  
  # Proportion by SEX
  sex_est <- svyby(~I(Wvot == 1), ~as_factor(indsex), des[[ds]], svymean, vartype = "ci", keep.var = TRUE)
  names(sex_est)[1]<-"Category"
  sex_est<-sex_est|>select(Category,"I(Wvot == 1)TRUE","ci_l.I(Wvot == 1)TRUE","ci_u.I(Wvot == 1)TRUE"  )
  sex_est$Dataset <- ds
  
  # Combine
  results[[ds]] <- rbind(age_est, sex_est)
}  

plot_data <- bind_rows(results)
plot_data[,2:4]<-round(plot_data[,2:4]*100,1)
plot_data$Dataset<-as.factor(plot_data$Dataset)
levels(plot_data$Dataset)<-c(2001,2005,2015,2017,2019)
# Rename columns for ggplot
plot_data <- plot_data |>
  rename(Proportion = `I(Wvot == 1)TRUE`,
         CI_low = `ci_l.I(Wvot == 1)TRUE`,
         CI_high = `ci_u.I(Wvot == 1)TRUE`)

# Plotting
ggplot(plot_data, aes(x = Category, y = Proportion, group = Dataset)) +
  #  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high), size=.9, width = 0.2) +
  geom_text(aes(label = Proportion), hjust = -.5, size = 4) +
  facet_wrap(~Dataset) +
  labs(title = "Proportion who voted at the last general election, by age and sex",
       x = "General Election Year",
       y = "Percent voted with 95% CIs",
       caption="Weighted cross-sectional estimates, ELSA Waves 1, 3, 8, 9, 10 data") +
  theme_minimal() +
  theme(strip.text = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        plot.caption=element_text(hjust = 0),
        plot.title.size=element_text(size = 18))
```




## 6. Multivariate results

This section presents the results of four series of logistic regressions models of voting behaviour at the 2019 general elections:
  
1. Stepwise models including voting behaviour recorded at previous waves, and socio-economic characteristics
2. Stepwise models including  socio-economic characteristics only
3. Stepwise models including self-rated health, self-rated mental abilities, self-rated memory, financial situation, sense of loneliness, presence of an internet  connection, involvement in volunteering socio economic characteristiscs, and socio-economic characteristics
4. As 3. above,  alongside voting behaviour recorded at previous waves

All models we fitted using weights.

::: {.panel-tabset}

<!-- ### 5.1 Unweighted regression results - voting behaviour included -->
  
  <!-- This series of stepwise models explores the association between socio-demographic variables on voting behaviour at Wave 10 without using weights.  -->
  
  <!--```{r multiv} -->
  <!-- #| output: asis -->
  <!-- elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb.fr) & !is.na(dimarr.fr) &  -->
                                 <!--                         !is.na(edqual.fr)& !is.na(wpdes.fr) & !is.na(hehelf.fr)) -->
  <!-- reg<-list() -->
  
  <!-- reg[["a11"]]<-glm(VotGE19.fr ~ VotRec0.f, -->
                           <!--                   elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a12"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13a"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                            <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr, -->
                            <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a14"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a15"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  <!-- reg[["a16"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr+wpdes.fr, -->
                           <!--                   elsaw.r,family=binomial())|>   tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a17"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr+wpdes.fr+ -->
                           <!--                     hehelf.fr, -->
                           <!--                   elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a18"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr*AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr+wpdes.fr+ -->
                           <!--                     hehelf.fr, -->
                           <!--                   elsaw.r,family=binomial())|>  tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  
  <!-- tbl_merge(tbls=reg,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**", "**M8**")) -->
  <!-- # |>  -->
  <!-- #   modify_column_hide(columns =  -->
  <!-- #                      c(conf.low_1,conf.low_2,conf.low_3,conf.low_4,conf.low_5,conf.low_6,conf.low_7,conf.low_8,conf.low_9, -->
  <!-- # conf.high_1,conf.high_2,conf.high_3,conf.high_4,conf.high_5,conf.high_6,conf.high_7,conf.high_8,conf.high_9)) -->
  
  <!--``` -->
  <!-- #### Coefficient plot of  Model 9 -->
  
  <!--```{r plot} -->
  <!-- #| fig-width: 12 -->
  <!-- #| fig-height: 10 -->
  <!-- reg[["a18"]]|>plot() -->
  
  <!--``` -->
  
### 6.1 Models with socio-economic variables, including past voting behaviour


#### Stepwise models

```{r multiv_w}
#| output: asis


 elsaw$dimarr.fr<-relevel(elsaw$dimarr.fr,ref=2)
 elsaw$hhdtypb.fr<-relevel(elsaw$hhdtypb.fr,ref=5)
 elsaw$edqual.fr<-relevel(elsaw$edqual.fr,ref=3)
 elsaw$wpdes.fr<-relevel(elsaw$wpdes.fr,ref=4)


elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb.fr) & !is.na(dimarr.fr) &
                          !is.na(edqual.fr)& !is.na(wpdes.fr) & !is.na(VotRec0.fr) & !is.na(w10xwgt) & !is.na(VotGE19.fr )) 

regw<-list()

regw[["a11"]]<-glm(VotGE19.fr ~ VotRec0.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.fr ~ VotRec0.fr+
                     indsex.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a13"]]<-glm(VotGE19.fr ~ VotRec0.fr+
                     indsex.fr+AgeCat3.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a13a"]]<-glm(VotGE19.fr ~ VotRec0.fr+
                      indsex.fr+AgeCat3.fr+hhdtypb.fr,
                    weights=w10xwgt,
                    elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a14"]]<-glm(VotGE19.fr ~ VotRec0.fr+
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr,
                   weights=w10xwgt, 
                   elsaw.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a15"]]<-glm(VotGE19.fr ~ VotRec0.fr+
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+
                     edqual.fr,  weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


# regw[["a16"]]<-glm(VotGE19.fr ~ VotRec0.fr+
#                      indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ edqual.fr+wpdes.fr, 
#                      weights=w10xwgt, elsaw.r,family=binomial())|>   
#                    tbl_regression(exponentiate = TRUE, digits=1) |> 
#                     add_glance_table(include=c(AIC,logLik,nobs)) |> 
#                     add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

tmp17<-glm(VotGE19.fr ~ VotRec0.fr+
             indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr,
           weights=w10xwgt, elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) 


regw[["a17"]]<- tmp17 |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



tmp18<-glm(VotGE19.fr ~ VotRec0.fr+
             indsex.fr*AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr,
           weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, digits=1) 
regw[["a18"]]<- tmp18 |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**"))


```
#### Coefficient plot of Models 7 & 8

```{r plot_w}
#| fig-width: 12
#| fig-height: 10

tmp17 |>plot()

tmp18 |>plot()
```


<!-- ### 4.3 Unweighted regression results - voting behaviour not included -->
  
  <!-- This series of stepwise models explores the association between socio-demographic variables and  voting behaviour at Wave 10, not using weights. -->
  
  
  <!-- #### Stepwise models -->
  
  <!--```{r multiv.w} -->
  <!-- #| output: asis -->
  
  <!-- reg<-list() -->
  
  <!-- #reg[["a11"]]<-glm(VotGE19.fr ~ VotRec0.fr, -->
  <!-- #                  elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a12"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13a"]]<-glm(VotGE19.fr ~  -->
                            <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr, -->
                            <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  <!-- reg[["a14"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a15"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  <!-- reg[["a16"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr+wpdes.fr, -->
                           <!--                   elsaw.r,family=binomial())|>   tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a17"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr+wpdes.fr+ -->
                           <!--                     hehelf.fr, -->
                           <!--                   elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a18"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr*AgeCat3.fr+hhdtypb.fr+dimarr.fr+ -->
                           <!--                     edqual.fr+wpdes.fr+ -->
                           <!--                     hehelf.fr, -->
                           <!--                   elsaw.r,family=binomial())|>  tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  
  <!-- tbl_merge(tbls=reg,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**")) -->
  <!-- # |>   modify_column_hide(columns = c(conf.low_1,conf.low_2,conf.low_3,conf.low_4,conf.low_5,conf.low_6,conf.low_7,conf.low_8, -->
  <!-- # conf.high_1,conf.high_2,conf.high_3,conf.high_4,conf.high_5,conf.high_6,conf.high_7,conf.high_8)) -->
  
  <!--``` -->
  <!-- #### Coefficients plot of Model 8 -->
  
  <!--```{r plot.w} -->
  <!-- #| fig-width: 12 -->
  <!-- #| fig-height: 10 -->
  
  <!-- reg[["a18"]]|>plot() -->
  <!--``` -->
  
### 6.2 Models with socio-economic variables, without past voting behaviour
  
#### Stepwise models
  
```{r multiv_w.w}
#| output: asis

elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb.fr) & !is.na(dimarr.fr) &
                          !is.na(edqual.fr)& !is.na(wpdes.fr)  & !is.na(w10xwgt) & !is.na(VotGE19.fr )) 

regw<-list()

regw[["a12"]]<-glm(VotGE19.fr ~ 
                     indsex.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>                   
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13a"]]<-glm(VotGE19.fr ~ 
                      indsex.fr+AgeCat3.fr+hhdtypb.fr,
                    weights=w10xwgt,
                    elsaw.r,family=binomial())|>                  
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a14"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+
                     edqual.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



# regw[["a16"]]<-glm(VotGE19.fr ~
#                      indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+
#                      edqual.fr+wpdes.fr,
#                    weights=w10xwgt,
#                    elsaw.r,family=binomial())|>   
#                     tbl_regression(exponentiate = TRUE, digits=1) |>                   
#                     add_glance_table(include=c(AIC,logLik,nobs)) |> 
#                     add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+
             edqual.fr+wpdes.fr,
           weights=w10xwgt,
           elsaw.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE, digits=1) 



regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp18<-glm(VotGE19.fr ~ 
             indsex.fr*AgeCat3.fr+hhdtypb.fr+dimarr.fr+
             edqual.fr+wpdes.fr,
           weights=w10xwgt,
           elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, digits=1) 

regw[["a18"]] <- tmp18 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**","**M6**", "**M7**"))

```

#### Coefficients plot of Models 7 & 8

```{r plot_w.w}
#| fig-width: 12
#| fig-height: 10

tmp17 |>plot()

tmp18 |>plot()

```

### 6.3 Models with extra covariates, no past voting behaviour

#### Stepwise models

```{r extrav}
#| output: asis

elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb.fr) & !is.na(dimarr.fr) &
                          !is.na(edqual.fr)& !is.na(wpdes.fr) & !is.na(hehelf.fr) &
                          !is.na(cfmap.fr)& !is.na(cfmetm.fr)& !is.na(iafcon.fr)& !is.na(pscede.fr) &
                          !is.na(hobb.fr) & !is.na(erfvol.f) & !is.na(w10xwgt) & !is.na(VotGE19.fr ))  


regw<-list()


regw[["a11"]]<-glm((VotGE19.fr) ~
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr,
                   weights=w10xwgt,elsaw.r,family=binomial()) |>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = hehelf.fr) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr
                   +hehelf.fr+cfmap.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1, 
                 include = c("hehelf.fr","cfmap.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr+cfmap.fr+cfmetm.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,                  
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



regw[["a14"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ edqual.fr+wpdes.fr+
                     hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a16"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr+hobb.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr","hobb.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
             hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr+hobb.fr+erfvol.fr,
           weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1, 
                 include =c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr","hobb.fr","erfvol.fr")) 

regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**"))
```




#### Coefficients plot of Model 7

```{r plot_extrav
#| fig-width: 12
#| fig-height: 10
tmp17 |>plot()
```

### 6.4 Models with extra covariates, including past voting behaviour

#### Stepwise models

```{r extrav2 }
#| output: asis

elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb.fr) & !is.na(dimarr.fr) &
                          !is.na(edqual.fr)& !is.na(wpdes.fr) & !is.na(hehelf.fr) &
                          !is.na(cfmap.fr)& !is.na(cfmetm.fr)& !is.na(iafcon.fr)& !is.na(pscede.fr) &
                          !is.na(hobb.fr) & !is.na(erfvol.f) & !is.na(w10xwgt) & !is.na(VotRec0.fr) & !is.na(VotGE19.fr ))  


regw<-list()


regw[["a11"]]<-glm((VotGE19.fr) ~
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr,
                   weights=w10xwgt,elsaw.r,family=binomial()) |>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = hehelf.fr) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr
                   +hehelf.fr+cfmap.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1, 
                 include = c("hehelf.fr","cfmap.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr+cfmap.fr+cfmetm.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,                  
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



regw[["a14"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+ edqual.fr+wpdes.fr+
                     hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a16"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
                     hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr+hobb.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr","hobb.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
             hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr+hobb.fr+erfvol.fr,
           weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1, 
                 include =c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr","hobb.fr","erfvol.fr")) 

regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp18<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb.fr+dimarr.fr+edqual.fr+wpdes.fr+
             hehelf.fr +cfmap.fr+cfmetm.fr+iafcon.fr+pscede.fr+hobb.fr+erfvol.fr+
             VotRec0.fr,
           weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1, 
                 include =c("hehelf.fr","cfmap.fr","cfmetm.fr","iafcon.fr","pscede.fr","hobb.fr","erfvol.fr","VotRec0.fr")) 

regw[["a18"]] <- tmp18 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**"))
```

#### Coefficients plot of Model 7

```{r plot_extrav2}
#| fig-width: 12
#| fig-height: 10
tmp18 |>plot()
```
:::
  
  
  
  
  
  
  <!--   ############################################################################################ -->
  <!--  ## Variable search -->
  
  
  
  <!--   vlab.m<-"" -->
  <!-- for (vr in names(elsaw)) { -->
      <!--   vlab.m<-c(vlab.m,paste(vr,attr(elsaw[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab0<-"" -->
  <!-- for (vr in names(elsa0)) { -->
      <!--   vlab0<-c(vlab0,paste(vr,attr(elsa0[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab.e1<-"" -->
  <!-- for (vr in names(elsa1)) { -->
      <!--   vlab.e1<-c(vlab.e1,paste(vr,attr(elsa1[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab.e3<-"" -->
  <!-- for (vr in names(elsa3)) { -->
      <!--   vlab.e3<-c(vlab.e3,paste(vr,attr(elsa3[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!--    vlab.e5<-"" -->
  <!--    for (vr in names(elsa5)) { -->
      <!--       <!-- vlab.e5<-c(vlab.e5,paste(vr,attr(elsa5[[vr]],"label"),sep="----")) -->
        <!--         <!-- } -->
  <!--   # -->
  <!--   vlab.e8<-"" -->
  <!-- for (vr in names(elsa8)) { -->
      <!--   vlab.e8<-c(vlab.e8,paste(vr,attr(elsa8[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab.e10<-"" -->
  <!-- for (vr in names(elsa10)) { -->
      <!--   vlab.e10<-c(vlab.e10,paste(vr,attr(elsa10[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  
  
  <!-- res.voted1<-grep("voted",vlab.e1,fixed=TRUE,value=T)  -->
  <!-- res.voted3<-grep("voted",vlab.e3,fixed=TRUE,value=T) -->
  <!-- res.voted5<-grep("voted",vlab.e5,fixed=TRUE,value=T) -->
  <!-- res.voted8<-grep("voted",vlab.e8,fixed=TRUE,value=T) -->
  
  <!-- res.age<-grep(" age",vlab.m,fixed=TRUE,value=T) -->
  <!-- res.voted10<-grep("voted",vlab.m,fixed=TRUE,value=T) -->
  <!-- res.class<-grep("class",vlab.m,value=T) -->
  <!-- res.activ<-grep("activity",vlab.m,value=T) -->
  
  
  <!--  - Income (declies?) IASICK --> 
  
  <!--    6168	scorgpo	F2		Numeric -->
  <!--    6169	scorgnw	F2	Whether is a member of tenants groups, resident groups, neighbourhoold watch	Numeric -->
  <!--    6170	scorgrl	F2	Whether is a member of a church or other religious group	Numeric -->
  <!--    6171	scorgch	F2	Whether is a member of charitable associations	Numeric -->
  <!--    6172	scorged	F2	Whether is a member of education, arts or music groups or evening classes	Numeric -->
  <!--    6173	scorgsc	F2	Whether is a member of social clubs	Numeric -->
  <!--    6174	scorgsp	F2	Whether is a member of sports clubs, gyms, exercise classes	Numeric -->
  <!--    6175	scorg95	F2	Whether is a member of other organisations, club or societies	Numeric -->
  <!--    6176	scorg96	F2	Respondent is not a member of any organisations, clubs or societies	Numeric -->
  <!--    6177	scorgn	F2	Number of committee meetings attends in a year	Numeric -->
  