---
title: "ELSA voting patterns study"
subtitle: Exploratory analysis  - draft version 2
author: "Pierre Walthéry"
date: today
date-format: DD MMMM YYYY
format: 
  html:
    embed-resources: true
#  odt: default
editor: source
execute:
  warning: false
  message: false
  echo: false
  cache: false
---

# Introduction
This document presents frequency and contingency tables as well as  regression output for a series of variables
from the English Longitudinal Study of Ageing - ELSA Wave 10, looking at their pattern of association with voting pattern at Wave 10.

Descriptive statistics  of all variables taken into account in the analysis is presented in Appendix 1.  


```{r data}

rm(list=ls())

 

ivs<-c("indsex","tenureb", "dimarr","hhdtypb","w10nssec5","wpdes","edqual", "ethnic", "scorgrl",  "hehelf","cfmap", "cfmetm","VotGE01","VotGE05","VotGE15","VotGE17", "headlba", "headlbe","iafcon", "exrela","iafind", "pscedd", "pscede", "spcar", "sptraa", "splift", "hobb","erfvol","scorgpo")

extrav<-c("VotRec0","VotRec01","VotGE19","wpdes5","edqual4","dimarr4", "hhdtypb4","srh4")

library(haven)
library(survey)
library(dplyr)
library(knitr)
library(gtsummary)
datadir<-"~/Data/elsa/UKDA-5050-stata/stata/stata13_se/"
# elsa0<-read_dta(paste0(datadir,"wave_0_common_variables_v2.dta"))
# elsa.ifs<-read_dta(paste0(datadir,"wave_10_ifs_derived_variables.dta"))
# elsa<-read_dta(paste0(datadir,"wave_10_elsa_data_eul_v4.dta"))
# elsa1<-read_dta(paste0(datadir,"wave_1_core_data_v3.dta"))
# elsa3<-read_dta(paste0(datadir,"wave_3_elsa_data_v4.dta"))
# elsa8<-read_dta(paste0(datadir,"wave_8_elsa_data_eul_v2.dta"))
# elsa9<-read_dta(paste0(datadir,"wave_9_elsa_data_eul_v2.dta"))
# 
# elsa<-merge(elsa,elsa0|>
#                  select(idauniq,hhdtypb,tenureb,ethnic),
#                  by="idauniq",all.x=T,all.Y=F)
# elsa<-merge(elsa,elsa.ifs|>
#                  select(idauniq,edqual),
#                  by="idauniq",all.x=T,all.Y=F)
# 
# ### Voting
# vot1389<-merge(
#      merge(elsa1 |> select(idauniq,scptpa1),
#            elsa3 |> select(idauniq,scpt01),
#                  by="idauniq",all=T
#            ),
#       merge(elsa8 |> select(idauniq,scptrvt),
#             elsa9 |> select(idauniq,scptrvt),
#                  by="idauniq",all=T
#            ),
#            by="idauniq",all=T)
# 
# names(vot1389)[which(names(vot1389)=="scptpa1")]<-"VotGE01"
# names(vot1389)[which(names(vot1389)=="scpt01")]<-"VotGE05"
# names(vot1389)[which(names(vot1389)=="scptrvt.x")]<-"VotGE15"
# names(vot1389)[which(names(vot1389)=="scptrvt.y")]<-"VotGE17"
# 
# elsa<-merge(elsa, vot1389,
#              by="idauniq",all=T
#            )
# 
# 
# elsaw<-elsa|>filter(!is.na(w10xwgt)) |>
#            select(idauniq,ivs,exlo80, psagf, exrslf, indager, scsptrvt,w10xwgt)
# 
# write_dta(elsaw, "/tmp/elsaw.dta")

elsaw<-read_dta("/tmp/elsaw.dta")

###############################################################################################################
```

```{r functions}
tfactor<-function(v){
  droplevels(as_factor(v,"both"))
}

lookfor<-function(name,dset){
grep(name,names(dset),value=T)  
}

colPct<-function(tab){
round(
100*prop.table(tab,1),
1
)
}

rowPct<-function(tab){
round(
100*prop.table(tab,2),
2  
)
}
  uniPct<-function(tab){
round(
100*prop.table(tab),
2  
)
}

# Get Unweighted frequency tables
ufreq <- function(var) {
  # Create frequency table
  freq_table <- ftable(as.formula(paste0(var,".f~1")), data = elsaw)
  
  # Calculate percentages
  percents <- uniPct(freq_table)
  
  # Create a data frame with Label, Frequency, and Percentage (rounded to 1 digit)
  result <- data.frame(
    Label = levels(eval(parse(text=paste0("elsaw$",var,".f")))),
    Frequencies = round(as.vector(freq_table), 1),
    Percent = round(as.vector(percents), 1)
  )
  names(result)[1]<-attr(eval(parse(text=paste0("elsaw$",var))),"label")
  # Return the result
  return(result)
}

  
  
# Get weighted frequency tables
wfreq <- function(var) {
  # Create frequency table
  freq_table <- svytable(as.formula(paste0("~", var,".f")), design = elsaw.s)
  
  # Calculate percentages
  percents <- uniPct(freq_table)
  
  # Create a data frame with Label, Frequency, and Percentage (rounded to 1 digit)
  result <- data.frame(
    Label = names(freq_table),
    Freq = round(as.vector(freq_table), 1),
    Pct = round(as.vector(percents), 1)
  )
  names(result)[1]<-attr(eval(parse(text=paste0("elsaw$",var))),"label")
  # Return the result
  return(result)
}

wfreq.r <- function(var) {
  # Create frequency table
  freq_table <- svytable(as.formula(paste0("~", var,".fr")), design = elsaw.s)
  
  # Calculate percentages
  percents <- uniPct(freq_table)
  
  # Create a data frame with Label, Frequency, and Percentage (rounded to 1 digit)
  result <- data.frame(
    Label = names(freq_table),
    Freq = round(as.vector(freq_table), 1),
    Pct = round(as.vector(percents), 1)
  )
  names(result)[1]<-attr(eval(parse(text=paste0("elsaw$",var))),"label")
  # Return the result
  return(result)
}

```


 

```{r recode}
############################################################################################
## Renaming voting variables
names(elsaw)[which(names(elsaw)=="scsptrvt")]<-"VotGE19"



## Recode

elsaw<-elsaw|>mutate(
            AgeCat85.f=as.factor(case_when(
            indager>=50 & indager<65 ~ "50-64",
            indager>=65 & indager<75 ~ "65-74",
            indager>=75 & indager<85 ~ "75-84",
            indager>=85  ~ "85+"
            )),
            AgeCat80.f=as.factor(case_when(
            indager>=50 & indager<65 ~ "50-64",
            indager>=65 & indager<70 ~ "65-69",
            indager>=70 & indager<75 ~ "70-74",
            indager>=75 & indager<80 ~ "75-79",
            indager>=80  ~ "80+"
            )),
            AgeCat2.f=as.factor(case_when(
            indager>=50 & indager<70 ~ "50-69",
            indager>=70 ~ "70+"
            )),
            AgeCat3.f=as.factor(case_when(
            indager>=50 & indager<70 ~ "50-69",
            indager>=70 & indager<80 ~ "70-79",
            indager>=80  ~ "80+"
            )),
            wpdes5=as.factor(case_when(
            wpdes==1 | wpdes==96 ~ "Retired (inc part)",
            wpdes==2 | wpdes==3~ "In enployment",
            wpdes==4 | wpdes==6~ "FT carer + unemp.",
            wpdes==5 ~ "LT sick/disabled"
            )),            
            edqual4=as.factor(case_when(
            edqual==1 | edqual==2 ~ "Tertiary",
            edqual==3 | edqual==4  | edqual==5 ~ "Secondary",
            edqual==6 ~ "Foreign",
            edqual==7 ~ "No qualifications"
            )),
            dimarr4=as.factor(case_when(
            dimarr==1  ~ "Single",
            dimarr==2 | dimarr==3 ~ "Married/SP",
            dimarr==4 | dimarr==5 ~ "Divorced/separated",
            dimarr==6 ~ "Widowed"
            )),
            hhdtypb4=as.factor(case_when(
            hhdtypb==1  | hhdtypb==7 ~ "Single person HH",
            hhdtypb==2 | dimarr==6 ~ "Two adults HH",
            hhdtypb==3 | dimarr==4 ~ "Family, large or small ",
            hhdtypb==5 ~ "Large adult HH"
            )),
            srh4=as.factor(case_when(
            hehelf==1  | hehelf==2 ~ "Excel/V. good",
            hehelf==3 ~ "Good",
            hehelf==4  ~ "Fair",
            hehelf==5 ~ "Poor"
            ))
          )            
            


#### Voting record - 2001-2017 
for(l in c("VotGE01","VotGE05","VotGE15","VotGE15","VotGE17")){
tmp<-as.numeric(eval(parse(text=paste0("elsaw$",l))))
elsaw[paste0(l,".n")]<-ifelse(tmp<0 | is.na(tmp),0,tmp)  
}

### Raw GE voting number
elsaw$votrec<-elsaw$VotGE01.n+elsaw$VotGE05.n+elsaw$VotGE15.n+elsaw$VotGE17.n

### Factor version, 3 cat 
elsaw<-elsaw|>mutate(VotRec0=case_when(
                                votrec==0 ~ "None", 
                                votrec==1 | votrec==2 ~ "1-2",
                                votrec==3 | votrec==4 ~ "3-4"),
                     VotRec01=case_when(
                                votrec==0 | votrec==1~ "None or 1", 
                                votrec==2 ~ "2",
                                votrec==3 | votrec==4 ~ "3-4"),
                     )

attr(elsaw$AgeCat80.f,"label")<-"Banded age, five categories"
attr(elsaw$AgeCat85.f,"label")<-"Banded age, four categories"
attr(elsaw$AgeCat2.f,"label")<-"Banded age, two categories"
attr(elsaw$AgeCat3.f,"label")<-"Banded age, three categories"
attr(elsaw$wpdes5,"label")<-"Recoded economic activity"
attr(elsaw$edqual4,"label")<-"Recoded education 4 categories"
attr(elsaw$dimarr4,"label")<-"Recoded marital status 4 categories"
attr(elsaw$hhdtypb4,"label")<-"Recoded household type, 4 categories"
attr(elsaw$VotRec0,"label")<-"Voting record, separate none"
attr(elsaw$VotRec01,"label")<-"Voting record, 0-1 together"


```



```{r factor}
for (hav in c(ivs,extrav)) {
elsaw<-cbind(elsaw,tmp=tfactor(
                      eval(
                      parse(
                        text=paste0("elsaw$",hav)))))
names(elsaw)[ncol(elsaw)]<-paste0(hav,".f")
}

```




```{r miscrec}
for(v  in c(paste0(ivs,".f"),paste0(extrav,".f"),"AgeCat2.f","AgeCat3.f")) {
elsaw<-elsaw|>mutate(
eval(
parse(
text=paste0(  
    v,"r=as.factor(case_when(",v,"==\"[-9] Refusal (8)\"       ~ NA_character_,",
    v,"==\"[-8] Don\'t know (9)\"                              ~ NA_character_,",
    v,"==\"[-8] Don\'t know\"                                  ~ NA_character_,",
    v,"==\"[-8] don\'t know\"                                 ~ NA_character_,",
    v,"==\"[-9] Refused\"                                      ~ NA_character_,",
    v,"==\"[-9] Refusal\"      ~ NA_character_,",
    v,"==\"[-9] refusal\"      ~ NA_character_,",
    v,"==\"[96] SPONTANEOUS: Semi-retired\"                    ~ NA_character_,",
    v,"==\"[86] Irrelevant answer - not codeable 01-06 or 96\" ~ NA_character_,",
    v,"==\"[85] Other answer - not codeable 01-06 or 96\"      ~ NA_character_,",
    v,"==\"[6] SPONTANEOUS - do not currently use\"      ~ NA_character_,",
    v,"==\"[85] Other answer - not codeable 01-04\"      ~ NA_character_,",
    v,"==\"[-2] Self-completion instrument not completed\"      ~ NA_character_,",
    v,"==\"[-1] Item not applicable\"      ~ NA_character_,",
    v,"==\"[-1] Item not applicable\"                               ~ NA_character_,",
    v,"==\"[-1] Not applicable\"                               ~ NA_character_,",
    v,"==\"[-9] Not answered (99)\"      ~ NA_character_,",
    v,"==\"[-9] Not answered\"      ~ NA_character_,",
    v,"==\"[-3] No valid answer\"      ~ NA_character_,",
    v,"==\"[99] Other\"      ~ NA_character_,",
    v,"==\"[-2] not asked\"      ~ NA_character_,",
    v,"==\"[-3] Incomplete/No job info collected\"      ~ NA_character_,",
    v,"==\"[-9] No answer/refused\"      ~ NA_character_,",
    ".default =",v,"))"
      )
)
      ))
      
names(elsaw)[ncol(elsaw)]<-paste0(v,"r")
}

levels(elsaw$VotGE19.fr)[c(1,2)]<-c("Didn't vote","Voted")

``` 




## 1. Variables used

|Name|Description|Variable label
|----|-----------|------------------------------------:
Age  4 categories  | AGECAT80    | `{r} attr(elsaw$AgeCat80, "label")`
Age 4 categories  | AGECAT85    | `{r} attr(elsaw$AgeCat85, "label")`
Sex  | INDSEX    | `{r} attr(elsaw$indsex, "label")`
Marital status|DIMARR [Need recoding]|`{r} attr(elsaw$dimarr, "label")`
Household type (Remove other)| hhdtypb|`{r} attr(elsaw$hhdtypb, "label")`
Social class – NS-SEC | W10NSSEC5|`{r} attr(elsaw$w10nssec5, "label")`
Main activity ..retired/employed etc (Remove Other)| WPDES|`{r} attr(elsaw$wpdes, "label")`
Education/highest qual. (Recode as previous article) | EDQUAL|`{r} attr(elsaw$edqual, "label")`
Ethnicity | ETHNIC|`{r} attr(elsaw$ethnic, "label")`
Religion | SCORGRL|`{r} attr(elsaw$scorgrl, "label")`
General Health| HEHELF|`{r} attr(elsaw$hehelf, "label")`
Mental Health| CFMAP (Recode into 3 Very good, Good, Fair,Poor)|`{r} attr(elsaw$cfmap, "label")`
Memory issues| CFMETM|`{r}  attr(elsaw$cfmetm, "label")`
Past voting behaviour|VotGE1,VotGE3,VotGE8,VotGE9|Voted in the past (from previous waves 1, 3, 8, 9, 10)`
Voted at the GE|SCSPTRVT|`{r}  attr(elsaw$scsptrvt, "label")`
Capacity everyday activities|HEADLB|`{r}  attr(elsaw$headlb, "label")`
Financial security|IAFCON,IAFINS,EXRELA|`{r}  attr(elsaw$ervol, "label")`
Control|IAFIND|`{r}  attr(elsaw$iafind, "label")`
Financial future | EXRSLF|`{r}  attr(elsaw$exrslf, "label")`
Happiness | PSCEDD|`{r}  attr(elsaw$pscedd, "label")`
Age perception | PSAGF|`{r}  attr(elsaw$psagf, "label")`
Social isolation | PSCEDE|`{r}  attr(elsaw$pscede, "label")`
Use of car | SPCAR|`{r}  attr(elsaw$spcar, "label")`
Use of public transport | SPTRAA|`{r}  attr(elsaw$sptraa, "label")`
Lift from friends | SPLIFT|`{r}  attr(elsaw$splift, "label")`
Grandchildren|DIGRAN |`{r}  attr(elsaw$digran, "label")`
Internet use | HOBB|`{r}  attr(elsaw$hobb, "label")`
Life expectancy expectation | EXLO80|`{r}  attr(elsaw$exlo80, "label")`
Volunteering | ERFVOL|`{r}  attr(elsaw$erfvol, "label")`
Caring responsibility| |`{r}  attr(elsaw$ervol, "label")`
Civic engagement|SCORGPO|`{r}  attr(elsaw$scorgpo, "label")`
Weights | w10w1lwgt | Wave 10 Longitudinal weight (wave 1 base)"                                      
Weights | w10w4lwgt | Wave 10 Longitudinal weight (wave 4 base)"                                      
Weights |w10xwgt | Wave 10 cross-sectional weight"                                                   
Weights |w10scwt | Wave 10 main self-completion weight"  


- Interest in politics
- Values


<!-- - Other activities: WPACT -->


## 2. Variables recoding 

### Recoding schemes:

1. Household type (HHDTYPB):

- Single person (adult) households
- Families (large + small)
- 2 adults households
- Large adults HH


2. Marital status (DIMARR)

- Single/never married
- Married
- Separated/dicvorced/widowed

3. Employment status (WPDES)

- Retired + looking after family/home
- In employment 
- Long term sick + unemployed

4. Highest qualification (EDQUAL)

- Detailed version

  - Degree or equivalent 
  - Higher ed below degree
  - A level or equivalent
  - GCSE or equivalent
  - Foreign
  - No qualification

- Short version

  - Higher education 
  - Secondary education
  - Foreign
  - No qualification



#### ELSA fieldwork dates

|Name|Fieldwork|Sample|Of which core|Vote asked|Last GE
|----|---------|-----------|-------|------|-------:
Wave 1 | 2002-03 | 12,100|11,391|Yes|June 2001 
Wave 2 |2004/05 |9,432|8,780|No|June 2001
Wave 3 |2006/07 |9,771|8,810|Yes|May 2005
Wave 4 |2008/09 |11,050|9,886|No|May 2005
Wave 5 |2010/11 | 10,274|9,090|No|May 2010
Wave 6 |2012/13 |10,601|9,169|No|May 2010
Wave 7 |2014/15 |9,666,|8,249|No|May 2010
Wave 8 |2016/17 |8,445| 7,223|Yes|May 2015
Wave 9|2018/19 |8,736| 7,289|Yes|June 2017
Wave 10|2021-23|-|-|Yes|Dec. 2019

Source: ELSA Wave 9 report, Table 1.1; Wikipedia.



### Recoding notes and issues

- There is potentially a large drop in the number of  obsersations resulting from  combining the voting records across waves: `{r} prettyNum(length(!is.na(elsaw$VotGE19)[!is.na(elsaw$VotGE01) | !is.na(elsaw$VotGE05) | !is.na(elsaw$VotGE15) | !is.na(elsaw$VotGE15)]),big.mark = ",")`. For this reason, missing values were coded as 0. As a result there may be a need to add a control for British vs non British citizenship. 
- Ethnic has `{r} prettyNum(table(is.na(elsaw$ethnic))[2],big.mark = ",")` missing values. I do not recommend using it.




## 3. Preliminary multivariate results

Confidence intervals removed for readability.

### 3.1 Unweighted regression results

```{r multiv}
#| output: asis
elsaw$edqual4.fr<-relevel(elsaw$edqual4.fr,ref=4)
elsaw$wpdes5.fr<-relevel(elsaw$wpdes5.fr,ref=2)
elsaw$VotRec0.f<-relevel(elsaw$VotRec0.f,ref=3)
elsaw$VotRec01.f<-relevel(elsaw$VotRec01.f,ref=3)
elsaw$srh4.fr<-relevel(elsaw$srh4.fr,ref=1)
attr(elsaw$edqual4.fr,"label")<-"Educational level"
attr(elsaw$wpdes5.fr,"label")<-"Economic activity"
attr(elsaw$VotRec0.f,"label")<-"Past voting record, v1"
attr(elsaw$VotRec01.f,"label")<-"Past voting record, v2"
attr(elsaw$srh4.fr,"label")<-"Self-rated health"
attr(elsaw$indsex.fr,"label")<-"Sex"
attr(elsaw$AgeCat3.fr,"label")<-"Age"
attr(elsaw$srh4.fr,"label")<-"*Self-rated health*"

reg<-list()

reg[["a11"]]<-glm((VotGE19.fr) ~ VotRec0.f,
                  elsaw,family=binomial())%>% tbl_regression(exponentiate = TRUE, digits=1)

reg[["a12"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr,
                  elsaw,family=binomial())%>%tbl_regression(exponentiate = TRUE, digits=1)

reg[["a13"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr,
                  elsaw,family=binomial())%>%tbl_regression(exponentiate = TRUE, digits=1)

reg[["a14"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr+
                    edqual4.fr,
                  elsaw,family=binomial())%>%tbl_regression(exponentiate = TRUE, digits=1)


reg[["a15"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr+
                    edqual4.fr+
                    wpdes5.fr,
                  elsaw,family=binomial())%>%   tbl_regression(exponentiate = TRUE, digits=1)

reg[["a16"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr+
                    edqual4.fr+
                    wpdes5.fr+
                    srh4.fr,
                  elsaw,family=binomial())%>% tbl_regression(exponentiate = TRUE, digits=1)

reg[["a17"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr*
                    AgeCat3.fr+
                    edqual4.fr+
                    wpdes5.fr+
                    srh4.fr,
                  elsaw,family=binomial())%>%  tbl_regression(exponentiate = TRUE, digits=1)



tbl_merge(tbls=reg,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**"))|> 
  modify_column_hide(columns = c(conf.low_1,conf.low_2,conf.low_3,conf.low_4,conf.low_5,conf.low_6,conf.low_7,conf.high_1,conf.high_2,conf.high_3,conf.high_4,conf.high_5,conf.high_6,conf.high_7))

```
#### Model 7, unweighted

```{r plot}
reg[["a17"]]|>plot()

```

### 3.2 Weighted regression results

```{r multiv_w}
#| output: asis

regw<-list()

regw[["a11"]]<-glm((VotGE19.fr) ~ VotRec0.f,
                    weights=w10xwgt,
                  elsaw,family=binomial())%>% tbl_regression(exponentiate = TRUE, digits=1)

regw[["a12"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr,
                    weights=w10xwgt,
                  elsaw,family=binomial())%>%tbl_regression(exponentiate = TRUE, digits=1)

regw[["a13"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr,
                    weights=w10xwgt,
                  elsaw,family=binomial())%>%tbl_regression(exponentiate = TRUE, digits=1)

regw[["a14"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr+
                    edqual4.fr,
                    weights=w10xwgt,
                  elsaw,family=binomial())%>%tbl_regression(exponentiate = TRUE, digits=1)


regw[["a15"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr+
                    edqual4.fr+
                    wpdes5.fr,
                  weights=w10xwgt,
                  elsaw,family=binomial())%>%   tbl_regression(exponentiate = TRUE, digits=1)

regw[["a16"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr+
                    AgeCat3.fr+
                    edqual4.fr+
                    wpdes5.fr+
                    srh4.fr,
                    weights=w10xwgt,
                  elsaw,family=binomial())%>% tbl_regression(exponentiate = TRUE, digits=1)

regw[["a17"]]<-glm((VotGE19.fr) ~ VotRec0.f+
                    indsex.fr*
                    AgeCat3.fr+
                    edqual4.fr+
                    wpdes5.fr+
                    srh4.fr,
                   weights=w10xwgt,
                  elsaw,family=binomial())%>%  tbl_regression(exponentiate = TRUE, digits=1)



tbl_merge(tbls=reg,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**"))|> 
  modify_column_hide(columns = c(conf.low_1,conf.low_2,conf.low_3,conf.low_4,conf.low_5,conf.low_6,conf.low_7,conf.high_1,conf.high_2,conf.high_3,conf.high_4,conf.high_5,conf.high_6,conf.high_7))

```
#### Model 7, weighted

```{r plot_w}
regw[["a17"]]|>plot()

```

## Appendix 1 Preliminary univariate and bivariate results

Results are presented as follows, under each tab below:

- Weighted frequencies and proportions of the original variables
- Weighted frequencies and proportions of the recoded (ie missing/invalid values removed) variables
- Contingency table of the variable with voting behaviour at Wave 10
- Chi-Squared test of independence.


::: panel-tabset


```{r univariates}
#| results: asis
#| echo: false

vars<-c(ivs,"wpdes5","edqual4","dimarr4", "hhdtypb4","VotRec0","VotRec01")

elsaw.s<-svydesign(~1,weights=~w10xwgt,data=elsaw)

# Apply the function to all  varsiables 
rslt.u <- lapply(vars, ufreq)
rslt.r <- lapply(vars, wfreq)
rslt.c <- lapply(vars, wfreq.r)


# Print the tables for each dependent varsiable using kable for better formatting
for (i in 1:length(rslt.c)) {
cat('\n')
cat('# ', vars[i], '\n')
#print(knitr::kable(vars[i],"html"))

cat('\n')
cat(paste0("#### ** Unweighted frequency table of unrecoded *",vars[i],"* **"))
cat('\n')
  
print(knitr::kable(rslt.u[[i]],"html"))

cat('\n')

################################################################################################

cat(paste0("#### **Weighted frequency table of unrecoded *",vars[i],"* **"))
cat('\n')
  
print(knitr::kable(rslt.r[[i]],"html"))

cat('\n')
cat(paste0("#### **Weighted frequency table of recoded *",vars[i],"* **"))
cat('\n')

print(knitr::kable(rslt.c[[i]],"html"))

################################################################################################

cat('\n\n')
cat(paste0("#### **Contingency table of  whether voted at the 2019 GE by ",vars[i],"* **"))
cat('\n')
print(kable(colPct(svytable(as.formula(paste0("~", vars[i],".fr","+VotGE19.fr")), elsaw.s))))

t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ VotGE19.fr")), elsaw.s)

print(t$method)
cat('\n')
print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
cat('\n')

################################################################################################


cat('\n\n')
if(vars[i]!="indsex"){
cat(paste0("#### **Contingency table of  Sex by *",vars[i],"* **"))
cat('\n')
print(kable(colPct(svytable(as.formula(paste0("~indsex.fr+", vars[i],".fr")), elsaw.s))))


t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ indsex.fr")), elsaw.s)

print(t$method)
cat('\n')
print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

cat('\n')
}
cat('\n\n')

cat(paste0("#### **Contingency table of  Age (2 cat) by *",vars[i],"* **"))
cat('\n')
print(kable(colPct(svytable(as.formula(paste0("~AgeCat2.fr+", vars[i],".fr")), elsaw.s))))

t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ AgeCat2.fr")), elsaw.s)

print(t$method)
cat('\n')
print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

cat('\n')

cat('\n\n')
cat(paste0("#### **Contingency table of  Age (3 cat) by *",vars[i],"* **"))
cat('\n')
print(kable(colPct(svytable(as.formula(paste0("~AgeCat3.fr+", vars[i],".fr")), elsaw.s))))

t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ AgeCat3.fr")), elsaw.s)

print(t$method)
cat('\n')
print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))

cat('\n')


}

cat('\n\n')
```

::: 



<!-- ############################################################################################ -->
<!-- <!-- ## Variable search --> -->

<!-- # vlab.m<-"" -->
<!-- # for (vr in names(elsaw)) { -->
<!-- # vlab.m<-c(vlab.m,paste(vr,attr(elsaw[[vr]],"label"),sep="----")) -->
<!-- # } -->
<!-- #  -->
<!-- # vlab0<-"" -->
<!-- # for (vr in names(elsa0)) { -->
<!-- # vlab0<-c(vlab0,paste(vr,attr(elsa0[[vr]],"label"),sep="----")) -->
<!-- # } -->
<!-- #  -->
<!-- # vlab.e1<-"" -->
<!-- # for (vr in names(elsa1)) { -->
<!-- # vlab.e1<-c(vlab.e1,paste(vr,attr(elsa1[[vr]],"label"),sep="----")) -->
<!-- # } -->
<!-- #  -->
<!-- # vlab.e3<-"" -->
<!-- # for (vr in names(elsa3)) { -->
<!-- # vlab.e3<-c(vlab.e3,paste(vr,attr(elsa3[[vr]],"label"),sep="----")) -->
<!-- # } -->
<!-- #  -->
<!-- # vlab.e8<-"" -->
<!-- # for (vr in names(elsa8)) { -->
<!-- # vlab.e8<-c(vlab.e8,paste(vr,attr(elsa8[[vr]],"label"),sep="----")) -->
<!-- # } -->
<!-- #  -->
<!-- #  -->
<!-- # res.voted1<-grep("voted",vlab.e1,fixed=TRUE,value=T) 12-->
<!-- # res.voted3<-grep("voted",vlab.e3,fixed=TRUE,value=T) -->
<!-- # res.voted8<-grep("voted",vlab.e8,fixed=TRUE,value=T) -->
<!-- #  -->
<!-- # res.age<-grep(" age",vlab.m,fixed=TRUE,value=T) -->
<!-- # res.voted10<-grep("voted",vlab.m,fixed=TRUE,value=T) -->
<!-- # res.class<-grep("class",vlab.m,value=T) -->
<!-- # res.activ<-grep("activity",vlab.m,value=T) -->


<!-- - Income (declies?) IASICK -->

<!-- 6168	scorgpo	F2		Numeric -->
<!-- 6169	scorgnw	F2	Whether is a member of tenants groups, resident groups, neighbourhoold watch	Numeric -->
<!-- 6170	scorgrl	F2	Whether is a member of a church or other religious group	Numeric -->
<!-- 6171	scorgch	F2	Whether is a member of charitable associations	Numeric -->
<!-- 6172	scorged	F2	Whether is a member of education, arts or music groups or evening classes	Numeric -->
<!-- 6173	scorgsc	F2	Whether is a member of social clubs	Numeric -->
<!-- 6174	scorgsp	F2	Whether is a member of sports clubs, gyms, exercise classes	Numeric -->
<!-- 6175	scorg95	F2	Whether is a member of other organisations, club or societies	Numeric -->
<!-- 6176	scorg96	F2	Respondent is not a member of any organisations, clubs or societies	Numeric -->
<!-- 6177	scorgn	F2	Number of committee meetings attends in a year	Numeric -->



