---
title: "ELSA voting patterns study"
subtitle: Exploratory analysis  - draft version 3
author: "Pierre Walthéry"
date: today
date-format: DD MMMM YYYY
format: 
  html:
   embed-resources: true
   page-layout: full
   mainfont: "Open Sans"
   toc: true
   smooth-scroll: true
   toc-location: left

#  odt: default
execute:
  warning: false
  message: false
  echo: false
  cache: false

---

## Introduction
This document presents preliminary descriptive,  uni-, bi-   and multivariate analysis   of voting at the 2019 General Elections  among the 50+, using  data from the English Longitudinal Study of Ageing - ELSA at Wave 10.

- Section 1 presents the variables included in the analysis
- Section 2 contains information about variable recoding and related issues
- Section 3 includes systematic unweighted and weighted univariate frequency tables
- Section 4 documents systematic unweighted and weighted contingency tables of the variables included in the analysis by votting behaviour at the 2019 general elections, age, sex. 
- Section 5 presents additional three way analysis of voting behaviour, age, sex and the year general elections took place.
- Section 6 presents the results of three series of logistic regression models of voting at the 2019 GE.




```{r data}

rm(list=ls())


ivs<-c("cfmap", "cfmetm","dimarr","edqual","erfvol","ethnic","exrela","headlba","headlbe","hehelf","hhdtypb","hobb","iafcon","iafind","indsex","pscedd","pscede","scorgpo","scorgrl","spcar","splift","sptraa","tenureb","VotGE01","VotGE05","VotGE15","VotGE17","w10nssec5","wpdes")

extrav<-c("VotRec0","VotRec01","VotGE19","wpdes5","edqual4","dimarr4", "hhdtypb4","srh4","iafcon4")

library(haven)
library(survey)
library(dplyr)
library(knitr)
library(gtsummary)
library(ggplot2)

datadir<-"~/Data/elsa/UKDA-5050-stata/stata/stata13_se/"

# elsa0<-read_dta(paste0(datadir,"wave_0_common_variables_v2.dta"))
# elsa.ifs<-read_dta(paste0(datadir,"wave_10_ifs_derived_variables.dta"))
# elsa1<-read_dta(paste0(datadir,"wave_1_core_data_v3.dta")) |> select(idauniq,scptpa1,indager,indsex,w1wgt)
# elsa3<-read_dta(paste0(datadir,"wave_3_elsa_data_v4.dta"))  |> select(idauniq,scpt01,indager,indsex,w3xwgt)
# elsa8<-read_dta(paste0(datadir,"wave_8_elsa_data_eul_v2.dta")) |> select(idauniq,scptrvt, indager,indsex,w8xwgt)
# elsa9<-read_dta(paste0(datadir,"wave_9_elsa_data_eul_v2.dta")) |> select(idauniq,scptrvt,indager,indsex,w9xwgt)
# elsa10<-read_dta(paste0(datadir,"wave_10_elsa_data_eul_v4.dta"))
# 
# voted<-list(
# GE01=elsa1,
# GE05=elsa3,
# GE15=elsa8,
# GE17=elsa9,
# GE19=elsa10 |> select(idauniq,scsptrvt,indager,indsex,w10xwgt)
# )
# 
# names(voted[["GE01"]])[which(names(voted[["GE01"]])=="scptpa1")]<-"Wvot"
# names(voted[["GE05"]])[which(names(voted[["GE05"]])=="scpt01")]<-"Wvot"
# names(voted[["GE15"]])[which(names(voted[["GE15"]])=="scptrvt")]<-"Wvot"
# names(voted[["GE17"]])[which(names(voted[["GE17"]])=="scptrvt")]<-"Wvot"
# names(voted[["GE19"]])[which(names(voted[["GE19"]])=="scsptrvt")]<-"Wvot"
# 
# 
# names(elsa1)[which(names(elsa1)=="scptpa1")]<-"VotGE01"
# names(elsa3)[which(names(elsa3)=="scpt01")]<-"VotGE05"
# names(elsa8)[which(names(elsa8)=="scptrvt")]<-"VotGE15"
# names(elsa9)[which(names(elsa9)=="scptrvt")]<-"VotGE17"
# 
# for(w in c(1,3,8,9)){
# tmp<-eval(parse(text=paste0("elsa",w)))
# names(tmp)[3:4]<-c(paste0("indager",w),paste0("indsex",w))
# eval(parse(text=paste0("elsa",w,"<-tmp")))
# }
# 
# elsaw<-merge(elsa10,elsa0|>
#                  select(idauniq,hhdtypb,tenureb,ethnic),
#                  by="idauniq",all.x=T,all.Y=F)
# 
# elsaw<-merge(elsaw,elsa.ifs|>
#                  select(idauniq,edqual),
#                  by="idauniq",all.x=T,all.Y=F)
# 
# ### Cross-sectional voting subsamples
# vot1389<-merge(
#      merge(elsa1,
#            elsa3,
#                  by="idauniq",all=T
#            ),
#       merge(elsa8 ,
#             elsa9 ,
#                  by="idauniq",all=T
#            ),
#            by="idauniq",all=T)
# 
# 
# vot13890<-merge(vot1389,elsa10 |> select(idauniq,scsptrvt,indager,indsex,w10xwgt) ,
#              by="idauniq",all=T
#            )
# 
# names(vot13890)[which(names(vot13890)=="scsptrvt")]<-"VotGE19"
# names(vot13890)[which(names(vot13890)=="indager")]<-"indager10"
# names(vot13890)[which(names(vot13890)=="indsex")]<-"indsex10"
# 
# names(elsaw)[which(names(elsaw)=="scsptrvt")]<-"VotGE19"
# 
# 
# elsaw<-merge(elsaw, vot1389,
#              by="idauniq",all=T
#            )
# 
# 
# elsaw<-elsaw|>filter(!is.na(w10xwgt)) |>
#            select(idauniq,all_of(ivs),exlo80, psagf, exrslf, indager, VotGE19,w10xwgt)
# 
# # Save the list to an RDS file
# saveRDS(voted, file = "/home/mscsepw2/Dropbox/work/ELSAwork/data/voted.rds")
# 
# write_dta(vot13890, "/home/mscsepw2/Dropbox/work/ELSAwork/data/elsal.dta")
# write_dta(elsaw, "/home/mscsepw2/Dropbox/work/ELSAwork/data/elsaw.dta")

elsaw<-read_dta("/home/mscsepw2/Dropbox/work/ELSAwork/data/elsaw.dta")
elsal<-read_dta("/home/mscsepw2/Dropbox/work/ELSAwork/data/elsal.dta")
voted <- readRDS("/home/mscsepw2/Dropbox/work/ELSAwork/data/voted.rds")

###############################################################################################################
```

```{r functions,tidy=T}
source("functions.R")
```



```{r recode}
############################################################################################
## Renaming voting variables
#elsaw$VotGE19<-elsaw$scsptrvt



## Recode

elsaw<-elsaw|>mutate(
  AgeCat85.f=as.factor(case_when(
    indager>=50 & indager<65 ~ "50-64",
    indager>=65 & indager<75 ~ "65-74",
    indager>=75 & indager<85 ~ "75-84",
    indager>=85  ~ "85+"
  )),
  AgeCat80.f=as.factor(case_when(
    indager>=50 & indager<65 ~ "50-64",
    indager>=65 & indager<70 ~ "65-69",
    indager>=70 & indager<75 ~ "70-74",
    indager>=75 & indager<80 ~ "75-79",
    indager>=80  ~ "80+"
  )),
  AgeCat2.f=as.factor(case_when(
    indager>=50 & indager<70 ~ "50-69",
    indager>=70 ~ "70+"
  )),
  AgeCat3.f=as.factor(case_when(
    indager>=50 & indager<70 ~ "50-69",
    indager>=70 & indager<80 ~ "70-79",
    indager>=80  ~ "80+"
  )),
  wpdes5=as.factor(case_when(
    wpdes==1 | wpdes==96 ~ "Retired (inc part)",
    wpdes==2 | wpdes==3~ "In employment",
    wpdes==4 | wpdes==6~ "FT carer + unemp.",
    wpdes==5 ~ "LT sick/disabled"
  )),            
  edqual4=as.factor(case_when(
    edqual==1 | edqual==2 ~ "Tertiary",
    edqual==3 | edqual==4  | edqual==5 ~ "Secondary",
    edqual==6 ~ "Foreign",
    edqual==7 ~ "No qualifications"
  )),
  dimarr4=as.factor(case_when(
    dimarr==1  ~ "Single",
    dimarr==2 | dimarr==3 ~ "Married/SP",
    dimarr==4 | dimarr==5 ~ "Divorced/separated",
    dimarr==6 ~ "Widowed"
  )),
  hhdtypb4=as.factor(case_when(
    hhdtypb==1  | hhdtypb==7 ~ "Single person HH",
    hhdtypb==2 | dimarr==6 ~ "Two adults HH",
    hhdtypb==3 | dimarr==4 ~ "Family, large or small ",
    hhdtypb==5 ~ "Large adult HH",
    .default = "Other"
  )),
  srh4=as.factor(case_when(
    hehelf==1  | hehelf==2 ~ "Excel/V. good",
    hehelf==3 ~ "Good",
    hehelf==4  ~ "Fair",
    hehelf==5 ~ "Poor"
  )),
    iafcon4=as.factor(case_when(
    iafcon==1   ~ "Manage very well",
    iafcon==2   ~ "Manage quite well",
    iafcon==3   ~ "Get by alright",
    iafcon==4 | iafcon==5 | iafcon==6 ~ "Does not manage well"
  ))

)            



#### Voting record - 2001-2017 
for(l in c("VotGE01","VotGE05","VotGE15","VotGE15","VotGE17")){
  tmp<-as.numeric(eval(parse(text=paste0("elsaw$",l))))
  elsaw[paste0(l,".n")]<-ifelse(tmp<0 | is.na(tmp),0,tmp)  
}

### Raw GE voting number
elsaw$votrec<-elsaw$VotGE01.n+elsaw$VotGE05.n+elsaw$VotGE15.n+elsaw$VotGE17.n

### Factor version, 3 cat 
elsaw<-elsaw|>mutate(VotRec0=case_when(
  votrec==0 ~ "None", 
  votrec==1 | votrec==2 ~ "1-2",
  votrec==3 | votrec==4 ~ "3-4"),
                     VotRec01=case_when(
    votrec==0 | votrec==1~ "None or 1", 
    votrec==2 ~ "2",
    votrec==3 | votrec==4 ~ "3-4"),
)

attr(elsaw$AgeCat80.f,"label")<-"Banded age, five categories"
attr(elsaw$AgeCat85.f,"label")<-"Banded age, four categories"
attr(elsaw$AgeCat2.f,"label")<-"Banded age, two categories"
attr(elsaw$AgeCat3.f,"label")<-"Banded age, three categories"
attr(elsaw$wpdes5,"label")<-"Recoded economic activity"
attr(elsaw$edqual4,"label")<-"Recoded education 4 categories"
attr(elsaw$dimarr4,"label")<-"Recoded marital status 4 categories"
attr(elsaw$hhdtypb4,"label")<-"Recoded household type, 4 categories"
attr(elsaw$VotRec0,"label")<-"Voting record, separate none"
attr(elsaw$VotRec01,"label")<-"Voting record, 0-1 together"


```


```{r factor}
for (hav in c(ivs,extrav)) {
  elsaw<-cbind(elsaw,tmp=tfactor(
    eval(
      parse(
        text=paste0("elsaw$",hav)))))
  names(elsaw)[ncol(elsaw)]<-paste0(hav,".f")
}

```


```{r miscrec}
for(v  in c(paste0(ivs,".f"),paste0(extrav,".f"),"AgeCat2.f","AgeCat3.f")) {
  elsaw<-elsaw|>mutate(
    eval(
      parse(
        text=paste0(  
          v,"r=as.factor(case_when(",v,"==\"[-9] Refusal (8)\"       ~ NA_character_,",
          v,"==\"[-8] Don\'t know (9)\"                              ~ NA_character_,",
          v,"==\"[-8] Don\'t know\"                                  ~ NA_character_,",
          v,"==\"[-8] don\'t know\"                                 ~ NA_character_,",
          v,"==\"[-9] Refused\"                                      ~ NA_character_,",
          v,"==\"[-9] Refusal\"      ~ NA_character_,",
          v,"==\"[-9] refusal\"      ~ NA_character_,",
          v,"==\"[96] SPONTANEOUS: Semi-retired\"                    ~ NA_character_,",
          v,"==\"[86] Irrelevant answer - not codeable 01-06 or 96\" ~ NA_character_,",
          v,"==\"[85] Other answer - not codeable 01-06 or 96\"      ~ NA_character_,",
          v,"==\"[6] SPONTANEOUS - do not currently use\"      ~ NA_character_,",
          v,"==\"[85] Other answer - not codeable 01-04\"      ~ NA_character_,",
          v,"==\"[-2] Self-completion instrument not completed\"      ~ NA_character_,",
          v,"==\"[-1] Item not applicable\"      ~ NA_character_,",
          v,"==\"[-1] Item not applicable\"                               ~ NA_character_,",
          v,"==\"[-1] Not applicable\"                               ~ NA_character_,",
          v,"==\"[-9] Not answered (99)\"      ~ NA_character_,",
          v,"==\"[-9] Not answered\"      ~ NA_character_,",
          v,"==\"[-3] No valid answer\"      ~ NA_character_,",
          v,"==\"[99] Other\"      ~ NA_character_,",
          v,"==\"[-2] not asked\"      ~ NA_character_,",
          v,"==\"[-3] Incomplete/No job info collected\"      ~ NA_character_,",
          v,"==\"[-9] No answer/refused\"      ~ NA_character_,",
          ".default =",v,"))"
        )
      )
    ))
  
  names(elsaw)[ncol(elsaw)]<-paste0(v,"r")
}

levels(elsaw$VotGE19.fr)[c(1,2)]<-c("Didn't vote","Voted")


elsaw$edqual4.fr<-relevel(elsaw$edqual4.fr,ref=4)
elsaw$wpdes5.fr<-relevel(elsaw$wpdes5.fr,ref=2)
elsaw$VotRec0.f<-relevel(elsaw$VotRec0.f,ref=3)
elsaw$VotRec01.f<-relevel(elsaw$VotRec01.f,ref=3)
elsaw$srh4.fr<-relevel(elsaw$srh4.fr,ref=1)
elsaw$dimarr4.fr<-relevel(elsaw$dimarr4.fr,ref=2)
elsaw$hhdtypb4.fr<-relevel(elsaw$hhdtypb4.fr,ref=5)

attr(elsaw$edqual4.fr,"label")<-"Educational level"
attr(elsaw$wpdes5.fr,"label")<-"Economic activity"
attr(elsaw$VotRec0.f,"label")<-"Past voting record, v1"
attr(elsaw$VotRec01.f,"label")<-"Past voting record, v2"
attr(elsaw$srh4.fr,"label")<-"Self-rated health"
attr(elsaw$indsex.fr,"label")<-"Sex"
attr(elsaw$AgeCat3.fr,"label")<-"Age"
attr(elsaw$srh4.fr,"label")<-"Self-rated health"
attr(elsaw$dimarr4.fr,"label")<-"Marital status"
attr(elsaw$hhdtypb4.fr,"label")<-"Household type"
attr(elsaw$cfmap.fr,"label")<-"Self-rated mental abilities"
attr(elsaw$cfmetm.fr,"label")<-"Self-rated memory"
attr(elsaw$iafcon4.fr,"label")<-"Financial situation"
attr(elsaw$pscede.fr,"label")<-"Feels lonely?"
attr(elsaw$hobb.fr,"label")<-"Internet connection?"
attr(elsaw$erfvol.fr,"label")<-"Volunteered"


``` 


## 1. Variables included

|Name|Description|Variable label
|----|-----------|------------------------------------:
Age  4 categories  | AGECAT80    | `{r} attr(elsaw$AgeCat80, "label")`
Age 4 categories  | AGECAT85    | `{r} attr(elsaw$AgeCat85, "label")`
Sex  | INDSEX    | `{r} attr(elsaw$indsex, "label")`
Marital status|DIMARR |`{r} attr(elsaw$dimarr, "label")`
Household type (Remove other)| hhdtypb|`{r} attr(elsaw$hhdtypb, "label")`
Social class – NS-SEC | W10NSSEC5|`{r} attr(elsaw$w10nssec5, "label")`
Main activity ..retired/employed etc (Remove Other)| WPDES|`{r} attr(elsaw$wpdes, "label")`
Education/highest qual. (Recode as previous article) | EDQUAL|`{r} attr(elsaw$edqual, "label")`
Ethnicity | ETHNIC|`{r} attr(elsaw$ethnic, "label")`
Religion | SCORGRL|`{r} attr(elsaw$scorgrl, "label")`
General Health| HEHELF|`{r} attr(elsaw$hehelf, "label")`
Mental Health| CFMAP (Recode into 3 Very good, Good, Fair,Poor)|`{r} attr(elsaw$cfmap, "label")`
Memory issues| CFMETM|`{r}  attr(elsaw$cfmetm, "label")`
Past voting behaviour|VotGE1,VotGE3,VotGE8,VotGE9|Voted in the past (from previous waves 1, 3, 8, 9, 10)`
Voted at the GE|SCSPTRVT|`{r}  attr(elsaw$scsptrvt, "label")`
Capacity everyday activities|HEADLB|`{r}  attr(elsaw$headlb, "label")`
Financial security|IAFCON,IAFINS,EXRELA|`{r}  attr(elsaw$ervol, "label")`
Control|IAFIND|`{r}  attr(elsaw$iafind, "label")`
Financial future | EXRSLF|`{r}  attr(elsaw$exrslf, "label")`
Happiness | PSCEDD|`{r}  attr(elsaw$pscedd, "label")`
Age perception | PSAGF|`{r}  attr(elsaw$psagf, "label")`
Social isolation | PSCEDE|`{r}  attr(elsaw$pscede, "label")`
Use of car | SPCAR|`{r}  attr(elsaw$spcar, "label")`
Use of public transport | SPTRAA|`{r}  attr(elsaw$sptraa, "label")`
Lift from friends | SPLIFT|`{r}  attr(elsaw$splift, "label")`
Grandchildren|DIGRAN |`{r}  attr(elsaw$digran, "label")`
Internet use | HOBB|`{r}  attr(elsaw$hobb, "label")`
Life expectancy expectation | EXLO80|`{r}  attr(elsaw$exlo80, "label")`
Volunteering | ERFVOL|`{r}  attr(elsaw$erfvol, "label")`
Caring responsibility| |`{r}  attr(elsaw$ervol, "label")`
Civic engagement|SCORGPO|`{r}  attr(elsaw$scorgpo, "label")`
Weights |w10xwgt | Wave 10 cross-sectional weight"                                                   


<!-- Weights | w10w1lwgt | Wave 10 Longitudinal weight (wave 1 base)"                                       -->
<!-- Weights | w10w4lwgt | Wave 10 Longitudinal weight (wave 4 base)"                                       -->
<!-- Weights |w10scwt | Wave 10 main self-completion weight"   -->
<!-- - Other activities: WPACT -->
  
  
## 2. Variables recoding 
  
### Recoding schemes:
  
1. Household type (HHDTYPB):
  
  - Single person (adult) households 
  - Families (large + small)
  - 2 adults households
  - Large adults HH


2. Marital status (DIMARR)

  - Single/never married
  - Married
  - Separated/dicvorced/widowed

3. Employment status (WPDES)

  - Retired + looking after family/home
  - In employment 
  -  Long term sick + unemployed

4. Highest qualification (EDQUAL)

  - Detailed version
  
    - Degree or equivalent 
    - Higher ed below degree
    - A level or equivalent
    - GCSE or equivalent
    - Foreign
    - No qualification

  - Short version
  
    - Higher education 
    - Secondary education
    - Foreign
    - No qualification


|Name|Fieldwork|Sample|Of which core|Vote asked|Last GE
|----|---------|-----------|-------|------|-------:
  Wave 1 | 2002-03 | 12,100|11,391|Yes|June 2001 
Wave 2 |2004/05 |9,432|8,780|No|June 2001
Wave 3 |2006/07 |9,771|8,810|Yes|May 2005
Wave 4 |2008/09 |11,050|9,886|No|May 2005
Wave 5 |2010/11 | 10,274|9,090|No|May 2010
Wave 6 |2012/13 |10,601|9,169|No|May 2010
Wave 7 |2014/15 |9,666,|8,249|No|May 2010
Wave 8 |2016/17 |8,445| 7,223|Yes|May 2015
Wave 9|2018/19 |8,736| 7,289|Yes|June 2017
Wave 10|2021-23|-|-|Yes|Dec. 2019
:Table 1: *ELSA fieldwork dates*
  Source: ELSA Wave 9 report, Table 1.1; Wikipedia.


#### Recoding notes and issues

- There is potentially a large drop in the number of  obsersations resulting from  combining the voting records across waves: `{r} prettyNum(length(!is.na(elsaw$VotGE19)[!is.na(elsaw$VotGE01) | !is.na(elsaw$VotGE05) | !is.na(elsaw$VotGE15) | !is.na(elsaw$VotGE15)]),big.mark = ",")`. For this reason, missing values were coded as 0. As a result there may be a need to add a control for British vs non British citizenship. 
- Ethnic has `{r} prettyNum(table(is.na(elsaw$ethnic))[2],big.mark = ",")` missing values. I do not recommend using it.


## 3. Univariates results

Results are presented as follows, under each tab below:
  
  1.  Unweighted frequencies and proportions of the original variables, unrecoded
  2.  Weighted frequencies and proportions of the recoded (ie missing/invalid values removed) variables

Please note that in the case of newly derived variable 1. and 2. will be identical 

::: {.panel-tabset}


```{r univariates}
#| results: asis
#| echo: false


vars<-c(ivs,"wpdes5","edqual4","dimarr4", "hhdtypb4","VotRec0","VotRec01")

elsaw.s<-svydesign(~1,weights=~w10xwgt,data=elsaw)

# Apply the function to all  variables 
rslt.u <- lapply(vars, ufreq)
rslt.r <- lapply(vars, wfreq)
rslt.c <- lapply(vars, wfreq.r)


# Print the tables for each dependent variable using kable for better formatting
for (i in 1:length(rslt.c)) {
   cat('### ', vars[i], '\n')
  
    cat(paste0("#### **Unweighted frequency table of unrecoded *",vars[i],"* **", '\n'))
    print(knitr::kable(rslt.u[[i]]),'html')
    cat('\n')
    
    cat(paste0("#### **Weighted frequency table of unrecoded *",vars[i],"* **", '\n'))
    print(knitr::kable(rslt.r[[i]]),'html')
     cat('\n')
     
    cat(paste0("#### **Weighted frequency table of recoded *",vars[i],"* **", '\n'))
    print(knitr::kable(rslt.c[[i]]),'html')
    cat('\n')

    }
cat('\n:::')
```




## 4. Bivariates results

This section contains, for each variable listed below:

  1. Contingency table with voting behaviour at Wave 10 with Chi-Squared test of independence.
  2. Contingency table with sex
  3. Contingency table with age, two categories
  4. Contingency table with sex, three categories

All contingency tables were computed with weighted data.

::: {.panel-tabset}

```{r biv}
#| results: asis
#| echo: false


for (i in 1:length(rslt.c)) {
  
   cat('### ', vars[i], '\n')
 
  cat(paste0("#### **Contingency table of  whether voted at the 2019 GE by ",vars[i],"* **"))

  tmp.t<-svytable(as.formula(paste0("~", vars[i],".fr+VotGE19.fr")), elsaw.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
  rownames(tmp.p)<-c("",rownames(tmp.t))
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(
    tmp.p
  ),'html')
  
  cat('\n')
  
  t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ VotGE19.fr")), elsaw.s)
  
  print(t$method)
  cat('\n')
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  cat('\n')
  
  ################################################################################################
  
  
  if(vars[i]!="indsex"){

    cat(paste0("#### **Contingency table of  Sex by *",vars[i],"* **"))
    cat('\n')
    
    tmp.t<-svytable(as.formula(paste0("~", vars[i],".fr+indsex.fr")), elsaw.s)
    tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
    tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
    rownames(tmp.p)<-c("",rownames(tmp.t))
    names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
    
    print(kable(tmp.p))
    cat('\n')
    
    t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ indsex.fr")), elsaw.s)
    
    print(t$method)
    cat('\n')
    print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
    
    cat('\n')
  }

  cat(paste0("#### **Contingency table of  Age (2 cat) by *",vars[i],"* **"))
  cat('\n')
  
  tmp.t<-svytable(as.formula(paste0("~", vars[i],".fr+AgeCat2.fr")), elsaw.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
  rownames(tmp.p)<-c("",rownames(tmp.t))
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ AgeCat2.fr")), elsaw.s)
  print(t$method)
  cat('\n')
  
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  cat('\n')
  
  cat(paste0("#### **Contingency table of  Age (3 cat) by *",vars[i],"* **"))
  cat('\n')
  tmp.t<-svytable(as.formula(paste0("~", vars[i],".fr+AgeCat3.fr")), elsaw.s)
  tmp.p<-data.frame(do.call(cbind, Map(cbind, as.data.frame.matrix(round(tmp.t,1)), as.data.frame.matrix(rowPct(tmp.t)))))
  tmp.p<-rbind(rep(c("Freq","%"),ncol(tmp.p)/2),tmp.p)
  rownames(tmp.p)<-c("",rownames(tmp.t))
  names(tmp.p)<-c(rbind(colnames(tmp.t)," "))
  
  print(kable(tmp.p))
  cat('\n')
  
  
  t<-svychisq(as.formula(paste0("~", vars[i],".fr","+ AgeCat3.fr")), elsaw.s)
  
  print(t$method)
  cat('\n')
  print(c(round(c(t$statistic,t$parameter[1], t$p.value),3)))
  
  cat('\n')
}
cat('\n:::')
```




## 5. Further descriptives
  
This section presents:

- Unweighted three way tables of age (two categories) and sex by whether voted at the 2019 general elections

- Cross-sectional proportions of 50+ who cast their ballot at the GE, by election year, sex and age 

###  5.1 Whether voted at  the 2019 GE by gender and age bands

#### Sample description

```{r desc}
#| output: asis

print(kable(
round((table(Age=elsaw$AgeCat2.fr,Sex=elsaw$indsex.fr,"Voted"=elsaw$VotGE19.fr))) 
),'html')
```

####  Weighted estimates:

- Women:
```{r descw}
#| output: asis

print(kable(
rbind(
    rowPct(svytable(~VotGE19.fr+AgeCat2.fr+indsex.fr,design = elsaw.s)[,,2]),
    c(100,100)
    )
)
)
```

- Men:

```{r descm}
#| output: asis

print(kable(
rbind(
rowPct(svytable(~VotGE19.fr+AgeCat2.fr+indsex.fr,design = elsaw.s)[,,1]),
    c(100,100)
    )
)
)
```

### 5.2 Voting pattern by age, sex and general election


```{r plotge}
#| fig-width: 12
#| fig-height: 10

for(ds in names(voted)) {
  voted[[ds]]<-voted[[ds]] |>mutate(AgeCat3.f=as.factor(case_when(
    indager>=50 & indager<70 ~ "50-69",
    indager>=70 & indager<80 ~ "70-79",
    indager>=80  ~ "80+"
  )))
}

results<-list()
des <- list(
  GE01 = svydesign(ids = ~1, weights = ~w1wgt, data=voted[["GE01"]] |>filter(!is.na(w1wgt))),
  GE05 = svydesign(ids = ~1, weights = ~w3xwgt, data=voted[["GE05"]] |>filter(!is.na(w3xwgt))),
  GE15 = svydesign(ids = ~1, weights = ~w8xwgt, data=voted[["GE15"]] |>filter(!is.na(w8xwgt))),
  GE17 = svydesign(ids = ~1, weights = ~w9xwgt, data=voted[["GE17"]] |>filter(!is.na(w9xwgt))),
  GE19 = svydesign(ids = ~1, weights = ~w10xwgt, data=voted[["GE19"]] |>filter(!is.na(w10xwgt)))
)

for(ds in names(des)) {
  age_est <- svyby(~I(Wvot == 1), ~AgeCat3.f, des[[ds]], svymean, vartype = "ci", keep.var = TRUE)
  names(age_est)[1]<-"Category"
  #  age_est$Category <- "AGE"
  #  age_est$Level <- as.factor(age_est$AGE)
  age_est<-age_est|>select(Category,"I(Wvot == 1)TRUE","ci_l.I(Wvot == 1)TRUE","ci_u.I(Wvot == 1)TRUE"  )
  age_est$Dataset <- ds
  
  # Proportion by SEX
  sex_est <- svyby(~I(Wvot == 1), ~as_factor(indsex), des[[ds]], svymean, vartype = "ci", keep.var = TRUE)
  names(sex_est)[1]<-"Category"
  sex_est<-sex_est|>select(Category,"I(Wvot == 1)TRUE","ci_l.I(Wvot == 1)TRUE","ci_u.I(Wvot == 1)TRUE"  )
  sex_est$Dataset <- ds
  
  # Combine
  results[[ds]] <- rbind(age_est, sex_est)
}  

plot_data <- bind_rows(results)
plot_data[,2:4]<-round(plot_data[,2:4]*100,1)
plot_data$Dataset<-as.factor(plot_data$Dataset)
levels(plot_data$Dataset)<-c(2001,2005,2015,2017,2019)
# Rename columns for ggplot
plot_data <- plot_data |>
  rename(Proportion = `I(Wvot == 1)TRUE`,
         CI_low = `ci_l.I(Wvot == 1)TRUE`,
         CI_high = `ci_u.I(Wvot == 1)TRUE`)

# Plotting
ggplot(plot_data, aes(x = Category, y = Proportion, group = Dataset)) +
  #  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = CI_low, ymax = CI_high), size=.9, width = 0.2) +
  geom_text(aes(label = Proportion), hjust = -.5, size = 4) +
  facet_wrap(~Dataset) +
  labs(title = "Proportion who voted at the last general election, by age and sex",
       x = "General Election Year",
       y = "Percent voted with 95% CIs",
       caption="Weighted cross-sectional estimates, ELSA Waves 1, 3, 8, 9, 10 data") +
  theme_minimal() +
  theme(strip.text = element_text(size = 18),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 14),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 16),
        plot.caption=element_text(hjust = 0),
        plot.title.size=element_text(size = 18))
```




## 6. Multivariate results

This section presents the results of four series of logistic regressions models of voting behaviour at the 2019 general elections:
  
1. Stepwise models including voting behaviour recorded at previous waves, and socio-economic characteristics
2. Stepwise models including  socio-economic characteristics only
3. Stepwise models including self-rated health, self-rated mental abilities, self-rated memory, financial situation, sense of loneliness, presence of an internet  connection, involvement in volunteering socio economic characteristiscs, and socio-economic characteristics
4. As 3. above,  alongside voting behaviour recorded at previous waves

All models we fitted using weights.

::: {.panel-tabset}

<!-- ### 5.1 Unweighted regression results - voting behaviour included -->
  
  <!-- This series of stepwise models explores the association between socio-demographic variables on voting behaviour at Wave 10 without using weights.  -->
  
  <!--```{r multiv} -->
  <!-- #| output: asis -->
  <!-- elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb4.fr) & !is.na(dimarr4.fr) &  -->
                                 <!--                         !is.na(edqual4.fr)& !is.na(wpdes5.fr) & !is.na(srh4.fr)) -->
  <!-- reg<-list() -->
  
  <!-- reg[["a11"]]<-glm(VotGE19.fr ~ VotRec0.f, -->
                           <!--                   elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a12"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13a"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                            <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr, -->
                            <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a14"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a15"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  <!-- reg[["a16"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr+wpdes5.fr, -->
                           <!--                   elsaw.r,family=binomial())|>   tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a17"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr+wpdes5.fr+ -->
                           <!--                     srh4.fr, -->
                           <!--                   elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a18"]]<-glm(VotGE19.fr ~ VotRec0.f+ -->
                           <!--                     indsex.fr*AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr+wpdes5.fr+ -->
                           <!--                     srh4.fr, -->
                           <!--                   elsaw.r,family=binomial())|>  tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  
  <!-- tbl_merge(tbls=reg,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**", "**M8**")) -->
  <!-- # |>  -->
  <!-- #   modify_column_hide(columns =  -->
  <!-- #                      c(conf.low_1,conf.low_2,conf.low_3,conf.low_4,conf.low_5,conf.low_6,conf.low_7,conf.low_8,conf.low_9, -->
  <!-- # conf.high_1,conf.high_2,conf.high_3,conf.high_4,conf.high_5,conf.high_6,conf.high_7,conf.high_8,conf.high_9)) -->
  
  <!--``` -->
  <!-- #### Coefficient plot of  Model 9 -->
  
  <!--```{r plot} -->
  <!-- #| fig-width: 12 -->
  <!-- #| fig-height: 10 -->
  <!-- reg[["a18"]]|>plot() -->
  
  <!--``` -->
  
### 6.1 Models with socio-economic variables, including past voting behaviour


#### Stepwise models

```{r multiv_w}
#| output: asis
elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb4.fr) & !is.na(dimarr4.fr) &
                          !is.na(edqual4.fr)& !is.na(wpdes5.fr) & !is.na(VotRec0.f) & !is.na(w10xwgt) & !is.na(VotGE19.fr )) 

regw<-list()

regw[["a11"]]<-glm(VotGE19.fr ~ VotRec0.f,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.fr ~ VotRec0.f+
                     indsex.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a13"]]<-glm(VotGE19.fr ~ VotRec0.f+
                     indsex.fr+AgeCat3.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a13a"]]<-glm(VotGE19.fr ~ VotRec0.f+
                      indsex.fr+AgeCat3.fr+hhdtypb4.fr,
                    weights=w10xwgt,
                    elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a14"]]<-glm(VotGE19.fr ~ VotRec0.f+
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr,
                   weights=w10xwgt, 
                   elsaw.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

regw[["a15"]]<-glm(VotGE19.fr ~ VotRec0.f+
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+
                     edqual4.fr,  weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


# regw[["a16"]]<-glm(VotGE19.fr ~ VotRec0.f+
#                      indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ edqual4.fr+wpdes5.fr, 
#                      weights=w10xwgt, elsaw.r,family=binomial())|>   
#                    tbl_regression(exponentiate = TRUE, digits=1) |> 
#                     add_glance_table(include=c(AIC,logLik,nobs)) |> 
#                     add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 

tmp17<-glm(VotGE19.fr ~ VotRec0.f+
             indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr,
           weights=w10xwgt, elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) 


regw[["a17"]]<- tmp17 |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



tmp18<-glm(VotGE19.fr ~ VotRec0.f+
             indsex.fr*AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr,
           weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, digits=1) 
regw[["a18"]]<- tmp18 |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**"))


```
#### Coefficient plot of Models 7 & 8

```{r plot_w}
#| fig-width: 12
#| fig-height: 10

tmp17 |>plot()

tmp18 |>plot()
```


<!-- ### 4.3 Unweighted regression results - voting behaviour not included -->
  
  <!-- This series of stepwise models explores the association between socio-demographic variables and  voting behaviour at Wave 10, not using weights. -->
  
  
  <!-- #### Stepwise models -->
  
  <!--```{r multiv.w} -->
  <!-- #| output: asis -->
  
  <!-- reg<-list() -->
  
  <!-- #reg[["a11"]]<-glm(VotGE19.fr ~ VotRec0.f, -->
  <!-- #                  elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a12"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a13a"]]<-glm(VotGE19.fr ~  -->
                            <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr, -->
                            <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  <!-- reg[["a14"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a15"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr, -->
                           <!--                   elsaw.r,family=binomial())|>tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  <!-- reg[["a16"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr+wpdes5.fr, -->
                           <!--                   elsaw.r,family=binomial())|>   tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a17"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr+wpdes5.fr+ -->
                           <!--                     srh4.fr, -->
                           <!--                   elsaw.r,family=binomial())|> tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  <!-- reg[["a18"]]<-glm(VotGE19.fr ~  -->
                           <!--                     indsex.fr*AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ -->
                           <!--                     edqual4.fr+wpdes5.fr+ -->
                           <!--                     srh4.fr, -->
                           <!--                   elsaw.r,family=binomial())|>  tbl_regression(exponentiate = TRUE, digits=1) |> add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) |>add_n() -->
  
  
  
  <!-- tbl_merge(tbls=reg,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**")) -->
  <!-- # |>   modify_column_hide(columns = c(conf.low_1,conf.low_2,conf.low_3,conf.low_4,conf.low_5,conf.low_6,conf.low_7,conf.low_8, -->
  <!-- # conf.high_1,conf.high_2,conf.high_3,conf.high_4,conf.high_5,conf.high_6,conf.high_7,conf.high_8)) -->
  
  <!--``` -->
  <!-- #### Coefficients plot of Model 8 -->
  
  <!--```{r plot.w} -->
  <!-- #| fig-width: 12 -->
  <!-- #| fig-height: 10 -->
  
  <!-- reg[["a18"]]|>plot() -->
  <!--``` -->
  
### 6.2 Models with socio-economic variables, without past voting behaviour
  
#### Stepwise models
  
```{r multiv_w.w}
#| output: asis

elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb4.fr) & !is.na(dimarr4.fr) &
                          !is.na(edqual4.fr)& !is.na(wpdes5.fr)  & !is.na(w10xwgt) & !is.na(VotGE19.fr )) 

regw<-list()

regw[["a12"]]<-glm(VotGE19.fr ~ 
                     indsex.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|> 
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>                   
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13a"]]<-glm(VotGE19.fr ~ 
                      indsex.fr+AgeCat3.fr+hhdtypb4.fr,
                    weights=w10xwgt,
                    elsaw.r,family=binomial())|>                  
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a14"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+
                     edqual4.fr,
                   weights=w10xwgt,
                   elsaw.r,family=binomial())|>
  tbl_regression(exponentiate = TRUE, digits=1) |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



# regw[["a16"]]<-glm(VotGE19.fr ~
#                      indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+
#                      edqual4.fr+wpdes5.fr,
#                    weights=w10xwgt,
#                    elsaw.r,family=binomial())|>   
#                     tbl_regression(exponentiate = TRUE, digits=1) |>                   
#                     add_glance_table(include=c(AIC,logLik,nobs)) |> 
#                     add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+
             edqual4.fr+wpdes5.fr,
           weights=w10xwgt,
           elsaw.r,family=binomial()) |>
  tbl_regression(exponentiate = TRUE, digits=1) 



regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp18<-glm(VotGE19.fr ~ 
             indsex.fr*AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+
             edqual4.fr+wpdes5.fr,
           weights=w10xwgt,
           elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, digits=1) 

regw[["a18"]] <- tmp18 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**","**M6**", "**M7**"))

```

#### Coefficients plot of Models 7 & 8

```{r plot_w.w}
#| fig-width: 12
#| fig-height: 10

tmp17 |>plot()

tmp18 |>plot()

```

### 6.3 Models with extra covariates, no past voting behaviour

#### Stepwise models

```{r extrav}
#| output: asis

elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb4.fr) & !is.na(dimarr4.fr) &
                          !is.na(edqual4.fr)& !is.na(wpdes5.fr) & !is.na(srh4.fr) &
                          !is.na(cfmap.fr)& !is.na(cfmetm.fr)& !is.na(iafcon4.fr)& !is.na(pscede.fr) &
                          !is.na(hobb.fr) & !is.na(erfvol.f) & !is.na(w10xwgt) & !is.na(VotGE19.fr ))  


regw<-list()


regw[["a11"]]<-glm((VotGE19.fr) ~
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr,
                   weights=w10xwgt,elsaw.r,family=binomial()) |>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = srh4.fr) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr
                   +srh4.fr+cfmap.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1, 
                 include = c("srh4.fr","cfmap.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr+cfmap.fr+cfmetm.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,                  
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



regw[["a14"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ edqual4.fr+wpdes5.fr+
                     srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a16"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr+hobb.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr","hobb.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
             srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr+hobb.fr+erfvol.fr,
           weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1, 
                 include =c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr","hobb.fr","erfvol.fr")) 

regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 




tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**"))
```




#### Coefficients plot of Model 7

```{r plot_extrav}
#| fig-width: 12
#| fig-height: 10
tmp17 |>plot()
```

### 6.4 Models with extra covariates, including past voting behaviour

#### Stepwise models

```{r extrav2}
#| output: asis

elsaw.r<-elsaw |>filter(!is.na(indsex.fr) & !is.na(AgeCat3.fr) & !is.na(hhdtypb4.fr) & !is.na(dimarr4.fr) &
                          !is.na(edqual4.fr)& !is.na(wpdes5.fr) & !is.na(srh4.fr) &
                          !is.na(cfmap.fr)& !is.na(cfmetm.fr)& !is.na(iafcon4.fr)& !is.na(pscede.fr) &
                          !is.na(hobb.fr) & !is.na(erfvol.f) & !is.na(w10xwgt) & !is.na(VotRec0.f) & !is.na(VotGE19.fr ))  


regw<-list()


regw[["a11"]]<-glm((VotGE19.fr) ~
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr,
                   weights=w10xwgt,elsaw.r,family=binomial()) |>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = srh4.fr) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a12"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr
                   +srh4.fr+cfmap.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1, 
                 include = c("srh4.fr","cfmap.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a13"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr+cfmap.fr+cfmetm.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,                  
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



regw[["a14"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+ edqual4.fr+wpdes5.fr+
                     srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a15"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr,
                   weights=w10xwgt, elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = TRUE, 
                 digits=1,
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


regw[["a16"]]<-glm(VotGE19.fr ~ 
                     indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
                     srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr+hobb.fr,
                   weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1,
                 include = c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr","hobb.fr")) |>
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp17<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
             srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr+hobb.fr+erfvol.fr,
           weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1, 
                 include =c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr","hobb.fr","erfvol.fr")) 

regw[["a17"]] <- tmp17 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 


tmp18<-glm(VotGE19.fr ~ 
             indsex.fr+AgeCat3.fr+hhdtypb4.fr+dimarr4.fr+edqual4.fr+wpdes5.fr+
             srh4.fr +cfmap.fr+cfmetm.fr+iafcon4.fr+pscede.fr+hobb.fr+erfvol.fr+
             VotRec0.f,
           weights=w10xwgt,elsaw.r,family=binomial())|>  
  tbl_regression(exponentiate = T, 
                 digits=1, 
                 include =c("srh4.fr","cfmap.fr","cfmetm.fr","iafcon4.fr","pscede.fr","hobb.fr","erfvol.fr","VotRec0.f")) 

regw[["a18"]] <- tmp18 |> 
  add_glance_table(include=c(AIC,logLik,nobs)) |> 
  add_significance_stars(hide_ci = F, hide_p = TRUE, hide_se = T) 



tbl_merge(tbls=regw,tab_spanner = c("**M1**", "**M2**", "**M3**", "**M4**", "**M5**", "**M6**", "**M7**", "**M8**"))
```

#### Coefficients plot of Model 7

```{r plot_extrav2}
#| fig-width: 12
#| fig-height: 10
tmp18 |>plot()
```
:::
  
  
  
  
  
  
  <!--   ############################################################################################ -->
  <!--  ## Variable search -->
  
  
  
  <!--   vlab.m<-"" -->
  <!-- for (vr in names(elsaw)) { -->
      <!--   vlab.m<-c(vlab.m,paste(vr,attr(elsaw[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab0<-"" -->
  <!-- for (vr in names(elsa0)) { -->
      <!--   vlab0<-c(vlab0,paste(vr,attr(elsa0[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab.e1<-"" -->
  <!-- for (vr in names(elsa1)) { -->
      <!--   vlab.e1<-c(vlab.e1,paste(vr,attr(elsa1[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab.e3<-"" -->
  <!-- for (vr in names(elsa3)) { -->
      <!--   vlab.e3<-c(vlab.e3,paste(vr,attr(elsa3[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!--    vlab.e5<-"" -->
  <!--    for (vr in names(elsa5)) { -->
      <!--       <!-- vlab.e5<-c(vlab.e5,paste(vr,attr(elsa5[[vr]],"label"),sep="----")) -->
        <!--         <!-- } -->
  <!--   # -->
  <!--   vlab.e8<-"" -->
  <!-- for (vr in names(elsa8)) { -->
      <!--   vlab.e8<-c(vlab.e8,paste(vr,attr(elsa8[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  <!-- vlab.e10<-"" -->
  <!-- for (vr in names(elsa10)) { -->
      <!--   vlab.e10<-c(vlab.e10,paste(vr,attr(elsa10[[vr]],"label"),sep="----")) -->
        <!-- } -->
  
  
  
  <!-- res.voted1<-grep("voted",vlab.e1,fixed=TRUE,value=T)  -->
  <!-- res.voted3<-grep("voted",vlab.e3,fixed=TRUE,value=T) -->
  <!-- res.voted5<-grep("voted",vlab.e5,fixed=TRUE,value=T) -->
  <!-- res.voted8<-grep("voted",vlab.e8,fixed=TRUE,value=T) -->
  
  <!-- res.age<-grep(" age",vlab.m,fixed=TRUE,value=T) -->
  <!-- res.voted10<-grep("voted",vlab.m,fixed=TRUE,value=T) -->
  <!-- res.class<-grep("class",vlab.m,value=T) -->
  <!-- res.activ<-grep("activity",vlab.m,value=T) -->
  
  
  <!--  - Income (declies?) IASICK --> 
  
  <!--    6168	scorgpo	F2		Numeric -->
  <!--    6169	scorgnw	F2	Whether is a member of tenants groups, resident groups, neighbourhoold watch	Numeric -->
  <!--    6170	scorgrl	F2	Whether is a member of a church or other religious group	Numeric -->
  <!--    6171	scorgch	F2	Whether is a member of charitable associations	Numeric -->
  <!--    6172	scorged	F2	Whether is a member of education, arts or music groups or evening classes	Numeric -->
  <!--    6173	scorgsc	F2	Whether is a member of social clubs	Numeric -->
  <!--    6174	scorgsp	F2	Whether is a member of sports clubs, gyms, exercise classes	Numeric -->
  <!--    6175	scorg95	F2	Whether is a member of other organisations, club or societies	Numeric -->
  <!--    6176	scorg96	F2	Respondent is not a member of any organisations, clubs or societies	Numeric -->
  <!--    6177	scorgn	F2	Number of committee meetings attends in a year	Numeric -->
  